---
title: "Analysis Code for the reproducibility checks of *A Bayesian Meta-Analysis of the Acoustic Properties of Infant-Directed Speech* "
author: 
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Semih Can Aktepe
   orcid: 0000-0002-4776-9138
   affiliations: University of Marburg
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    fig-align: "center"
    embed-resources: true
execute:
  message: false
  warning: false
  eval: false
---

This document contains the reproducibility checks. Changes to the original code are indicated by the initials of the first author ("BS"). 
An overview over results can be found in Sections R1 to R3. 

```{r setup, include=FALSE, eval=TRUE}
pacman::p_load(
  #general
  Rcpp,
  ggplot2,
  tidybayes,
  tidyverse,
  readxl,
  dplyr,
  moments,
  glue,
  tidybayes,
  Counterfactual,
  clickR,
  job,
  #metaanalysis
  metafor,
  robumeta,
  esc,
  effectsize,
  PublicationBias,
  #visualization
  ggplot2,
  ggridges,
  lattice,
  cowplot,
  RColorBrewer,
  forcats,
  ggalluvial,
  knitr,
  osfr,
  #modelfitting
  brms,
  boot,
  lme4,
  mice,
  pander,
  loo, 
  # put to the end due to conflicts
  here)
source(here("functions.R"))
```

```{r, include=FALSE}
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE, fig.width=12, fig.height=10, fig.fullwidth=TRUE)
```

\newpage
Folder & Data Setup
---------------

```{r, eval = FALSE}
#Use this chunk to set up the data and folder structure.
#If you are running the code on a computer with a Linux operating system, you can download the compiled 
#models from OSF. If not, a "models" folder will be made to make sure that the code can run on your computer:

# BS: Had to take this out of the loop so that the following code runs
  project_files <- osf_retrieve_node("https://osf.io/hc7me/") #Note that this requires about 12 GB
  project_models_list <- osf_ls_files(project_files)

if (Sys.info()['sysname'] == "Linux") {
  dir.create("models")
  osf_download(osf_ls_files(project_models_list[2, ]), path = "models", verbose = TRUE) #the models have to be downloaded in separate folders from OSF
  osf_download(osf_ls_files(project_models_list[6, ]), path = "models", verbose = TRUE)
  osf_download(osf_ls_files(project_models_list[5, ]), path = "models", verbose = TRUE)
  osf_download(osf_ls_files(project_models_list[3, ]), path = "models", verbose = TRUE)
} else {
 dir.create("models")
}

#The following code downloads the data and robustness checks data:
#BS: Wrong index here
project_data_list <- osf_ls_files(project_models_list[7,])
osf_download(project_data_list, path = "data")

robustness_data_list <- osf_ls_files(project_files)
osf_download(robustness_data_list[4, ])


```
number of cores available to run the models
```{r}
# cores <- parallel::detectCores()
cores <- 2
```


In the below script, I use the following abbreviations: 
      F0 = Fundamental Frequency, 
      VSA = Vowel Space Area, 
      AR = Articulation Rate, 
      VD = Vowel Duration, & 
      F0V = F0 Variability.

1: Intercepts-Only Models
---------------

Let's start with an intercepts-only model of F0, with nested effects:

```{r}
data_F0_multiple_final <- readRDS(here("data/data_F0_multiple_final.RData"))
data_F0_final <- readRDS(here("data/data_F0_final.RData"))

baseline_z <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + (1 | Language/id_site/measurement_num))

priors <- c(prior(normal(0, 2.5), class = Intercept),
            prior(normal(1, 1), class = sd),
            prior(gamma(2, 0.1), class = nu))

F0_intercept_m <- 
  brm_multiple(
    baseline_z,
    # save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final, 
    family = student,
    prior = priors,
    file = here("models", "replication", "F0_intercept_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = 2,  # BS: using all cores is useless when you have two chains and don't do within-chain parallelization
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))


pp_check(F0_intercept_m, ndraws = 100)
summary(F0_intercept_m)
```

```{r, fig.width=12, fig.height=15}
#extract data from the intercepts-only model:
study.draws <- spread_rvars(F0_intercept_m, `r_Language:id_site`[`r_Language`, ], b_Intercept) %>%
  mutate(b_Intercept = `r_Language:id_site` + b_Intercept) %>%
  mutate(r_Language = paste0(sapply(strsplit(as.character(r_Language), "[()]"), `[`,2),
                             "_",
                             sapply(strsplit(as.character(r_Language), "[()]"), `[`,3))) %>%
  mutate(r_Language = as.factor(r_Language)) %>%
  select(r_Language, b_Intercept)

pooled.effect.draws <- spread_rvars(F0_intercept_m, b_Intercept) %>%
  mutate(r_Language = "Pooled Effect") %>%
  mutate(r_Language = as.factor(r_Language)) %>%
  select(r_Language, b_Intercept)

forest.data <- rbind(study.draws, pooled.effect.draws) %>%
  ungroup() %>%
  mutate(r_Language = reorder(r_Language, b_Intercept))

forest.data.summary <- group_by(forest.data, r_Language) %>%
  mean_qi(b_Intercept)

#plot the results:
forest_plot_F0 <- ggplot(aes(dist = b_Intercept, y = relevel(r_Language, "Pooled Effect", after = Inf)), 
                         data = forest.data) +
  stat_dist_halfeye(fill = "steelblue", scale = 0.7, alpha = 0.8, size = 0.8, show_point = T) +
  geom_vline(xintercept = 0.0, color = "black", size = 0.3, linetype="dotted") +
  geom_text(data = mutate_if(forest.data.summary, is.numeric, round, 2), aes(label = glue("{b_Intercept} [{.lower}, {.upper}]"), x = Inf), hjust = "inward", size = 3) +
  labs(x = "placeholder", y = element_blank()) +
  scale_x_continuous("Effect Size (Hedges' g)", limits = c(-1, 6), breaks = c(0, 1, 2, 3, 4, 5)) +
  ggtitle(expression(paste("Forest Plot for Studies on ", italic(f)[o]))) +
  theme_bw()
forest_plot_F0 <- forest_plot_F0 + theme(plot.title = element_text(hjust = 0.5, size=15))
forest_plot_F0
```

Let's next build an intercepts-only model of VSA, with nested effects:

```{r}
data_VSA_multiple_final <- readRDS(here("data/data_VSA_multiple_final.RData"))
data_VSA_final <- readRDS(here("data/data_VSA_final.RData"))

VSA_intercept_m <- 
  brm_multiple(
    baseline_z,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_multiple_final, 
    family = student,
    prior = priors,
    file = here("models", "replication", "VSA_intercept_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))


pp_check(VSA_intercept_m, ndraws = 100)
summary(VSA_intercept_m)

```

```{r, fig.width=12, fig.height=15}
#extract data from the baseline model:
study.draws <- spread_rvars(VSA_intercept_m, `r_Language:id_site`[`r_Language`, ], b_Intercept) %>%
  mutate(b_Intercept = `r_Language:id_site` + b_Intercept) %>%
  mutate(r_Language = paste0(sapply(strsplit(as.character(r_Language), "[()]"), `[`,2),
                             "_",
                             sapply(strsplit(as.character(r_Language), "[()]"), `[`,3))) %>%
  mutate(r_Language = as.factor(r_Language)) %>%
  select(r_Language, b_Intercept)

pooled.effect.draws <- spread_rvars(VSA_intercept_m, b_Intercept) %>%
  mutate(r_Language = "Pooled Effect") %>%
  mutate(r_Language = as.factor(r_Language)) %>%
  select(r_Language, b_Intercept)

forest.data <- rbind(study.draws, pooled.effect.draws) %>%
  ungroup() %>%
  mutate(r_Language = reorder(r_Language, b_Intercept))

forest.data.summary <- group_by(forest.data, r_Language) %>%
  mean_qi(b_Intercept)

#plot the results:
forest_plot_VSA <- ggplot(aes(dist = b_Intercept, y = relevel(r_Language, "Pooled Effect", after = Inf)), data = forest.data) +
  stat_dist_halfeye(fill = "steelblue", scale = 0.7, alpha = 0.8, size = 0.8, show_point = F) +
  geom_point(data=forest.data.summary, color='black', shape=18, size=2, aes(x = b_Intercept, y = r_Language)) +
  geom_vline(xintercept = 0, color = "black", size = 0.3, linetype="dotted") +
  geom_text(data = mutate_if(forest.data.summary, is.numeric, round, 2), aes(label = glue("{b_Intercept} [{.lower}, {.upper}]"), x = Inf), hjust = "inward", size = 3) +
  labs(x = "placeholder", y = element_blank()) +
  scale_x_continuous("Effect Size (Hedges' g)", limits = c(-1.5, 4), breaks = c(0, 1, 2, 3, 4, 5)) +
  ggtitle("Forest Plot for Studies on Vowel Space Area") +
  theme_bw()
forest_plot_VSA <- forest_plot_VSA + theme(plot.title = element_text(hjust = 0.5, size=15))
forest_plot_VSA
```


Let's next build an intercepts-only model of AR, with nested effects:

```{r}
data_AR_multiple_final <- readRDS(here("data/data_AR_multiple_final.RData"))
data_AR_final <- readRDS(here("data/data_AR_final.RData"))

AR_intercept_m <- 
  brm_multiple(
    baseline_z,
    save_pars = save_pars(all = TRUE),
    data = data_AR_multiple_final, 
    family = student,
    prior = priors,
    file = here("models", "replication", "AR_intercept_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

# saveRDS(AR_intercept_m, here::here("models", "replication", "AR_intercept_m_rep.RDS"))

pp_check(AR_intercept_m, ndraws = 100)
summary(AR_intercept_m)

```

```{r, fig.width=12, fig.height=15}
#extract data from the baseline model:
study.draws <- spread_rvars(AR_intercept_m, `r_Language:id_site`[`r_Language`, ], b_Intercept) %>%
  mutate(b_Intercept = `r_Language:id_site` + b_Intercept) %>%
  mutate(r_Language = paste0(sapply(strsplit(as.character(r_Language), "[()]"), `[`,2),
                             "_",
                             sapply(strsplit(as.character(r_Language), "[()]"), `[`,3))) %>%
  mutate(r_Language = as.factor(r_Language)) %>%
  select(r_Language, b_Intercept)

pooled.effect.draws <- spread_rvars(AR_intercept_m, b_Intercept) %>%
  mutate(r_Language = "Pooled Effect") %>%
  mutate(r_Language = as.factor(r_Language)) %>%
  select(r_Language, b_Intercept)

forest.data <- rbind(study.draws, pooled.effect.draws) %>%
  ungroup() %>%
  mutate(r_Language = reorder(r_Language, b_Intercept))

forest.data.summary <- group_by(forest.data, r_Language) %>%
  mean_qi(b_Intercept)

#plot the results:
forest_plot_AR <- ggplot(aes(dist = b_Intercept, y = relevel(r_Language, "Pooled Effect", after = Inf)), data = forest.data) +
  stat_dist_halfeye(fill = "steelblue", scale = 0.7, alpha = 0.8, size = 0.8, show_point = T) +
  geom_vline(xintercept = 0, color = "black", size = 0.3, linetype="dotted") +
  geom_text(data = mutate_if(forest.data.summary, is.numeric, round, 2), aes(label = glue("{b_Intercept} [{.lower}, {.upper}]"), x = Inf), hjust = "inward", size = 3) +
  labs(x = "placeholder", y = element_blank()) +
  scale_x_continuous("Effect Size (Hedges' g)", limits = c(-4.5, 2.2), breaks = c(-3, -2, -1, 0, 1, 2)) +
  ggtitle("Forest Plot for Studies on Articulation Rate") +
  theme_bw()
forest_plot_AR <- forest_plot_AR + theme(plot.title = element_text(hjust = 0.5, size=15))
forest_plot_AR
```

Let's next build an intercepts-only model of VD, with nested effects:

```{r}
data_VD_multiple_final <- readRDS(here("data/data_VD_multiple_final.RData"))
data_VD_final <- readRDS(here("data/data_VD_final.RData"))

VD_intercept_m <- 
  brm_multiple(
    baseline_z,
    save_pars = save_pars(all = TRUE),
    data = data_VD_multiple_final, 
    family = student,
    prior = priors,
    file = here("models", "replication", "VD_intercept_m_rep"),
    sample_prior = T,
    iter = 10000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))

# saveRDS(VD_intercept_m, here::here("models", "replication", "VD_intercept_m_rep.RDS"))

pp_check(VD_intercept_m, ndraws = 100)
summary(VD_intercept_m)
```

```{r, fig.width=12, fig.height=15}
#extract data from the baseline model:
study.draws <- spread_rvars(VD_intercept_m, `r_Language:id_site`[`r_Language`, ], b_Intercept) %>%
  mutate(b_Intercept = `r_Language:id_site` + b_Intercept) %>%
  mutate(r_Language = paste0(sapply(strsplit(as.character(r_Language), "[()]"), `[`,2),
                             "_",
                             sapply(strsplit(as.character(r_Language), "[()]"), `[`,3))) %>%
  mutate(r_Language = as.factor(r_Language)) %>%
  select(r_Language, b_Intercept)

pooled.effect.draws <- spread_rvars(VD_intercept_m, b_Intercept) %>%
  mutate(r_Language = "Pooled Effect") %>%
  mutate(r_Language = as.factor(r_Language)) %>%
  select(r_Language, b_Intercept)

forest.data <- rbind(study.draws, pooled.effect.draws) %>%
  ungroup() %>%
  mutate(r_Language = reorder(r_Language, b_Intercept))

forest.data.summary <- group_by(forest.data, r_Language) %>%
  mean_qi(b_Intercept)

#plot the results:
forest_plot_VD <- ggplot(aes(dist = b_Intercept, y = relevel(r_Language, "Pooled Effect", after = Inf)), data = forest.data) +
  stat_dist_halfeye(fill = "steelblue", scale = 0.7, alpha = 0.8, size = 0.8, show_point = T) +
  geom_vline(xintercept = 0, color = "black", size = 0.3, linetype="dotted") +
  geom_text(data = mutate_if(forest.data.summary, is.numeric, round, 2), aes(label = glue("{b_Intercept} [{.lower}, {.upper}]"), x = Inf), hjust = "inward", size = 3) +
  labs(x = "placeholder", y = element_blank()) +
  scale_x_continuous("Effect Size (Hedges' g)", limits = c(-1, 3.4), breaks = c(-1, 0, 1, 2, 3)) +
  ggtitle("Forest Plot for Studies on Vowel Duration") +
  theme_bw()
forest_plot_VD <- forest_plot_VD + theme(plot.title = element_text(hjust = 0.5, size=15))
forest_plot_VD
```

Let's next build an intercepts-only model of F0V, with nested effects:

```{r}
data_F0V_multiple_final <- readRDS(here("data/data_F0V_multiple_final.RData"))
data_F0V_final <- readRDS(here("data/data_F0V_final.RData"))

F0V_intercept_m <- 
  brm_multiple(
    baseline_z,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_multiple_final, 
    family = student,
    prior = priors,
    file = here("models", "replication", "F0V_intercept_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))

# saveRDS(F0V_intercept_m, here::here("models", "replication", "F0V_intercept_m_rep.RDS"))

pp_check(F0V_intercept_m, ndraws = 100)
summary(F0V_intercept_m)
```

```{r, fig.width=12, fig.height=15}
#extract data from the baseline model:
study.draws <- spread_rvars(F0V_intercept_m, `r_Language:id_site`[`r_Language`, ], b_Intercept) %>%
  mutate(b_Intercept = `r_Language:id_site` + b_Intercept) %>%
  mutate(r_Language = paste0(sapply(strsplit(as.character(r_Language), "[()]"), `[`,2),
                             "_",
                             sapply(strsplit(as.character(r_Language), "[()]"), `[`,3))) %>%
  mutate(r_Language = as.factor(r_Language)) %>%
  select(r_Language, b_Intercept)

pooled.effect.draws <- spread_rvars(F0V_intercept_m, b_Intercept) %>%
  mutate(r_Language = "Pooled Effect") %>%
  mutate(r_Language = as.factor(r_Language)) %>%
  select(r_Language, b_Intercept)

forest.data <- rbind(study.draws, pooled.effect.draws) %>%
  ungroup() %>%
  mutate(r_Language = reorder(r_Language, b_Intercept))

forest.data.summary <- group_by(forest.data, r_Language) %>%
  mean_qi(b_Intercept)

#plot the results:
forest_plot_F0V <- ggplot(aes(dist = b_Intercept, y = relevel(r_Language, "Pooled Effect", after = Inf)), data = forest.data) +
  stat_dist_halfeye(fill = "steelblue", scale = 0.7, alpha = 0.8, size = 0.8, show_point = T) +
  geom_vline(xintercept = 0, color = "black", size = 0.3, linetype="dotted") +
  geom_text(data = mutate_if(forest.data.summary, is.numeric, round, 2), aes(label = glue("{b_Intercept} [{.lower}, {.upper}]"), x = Inf), hjust = "inward", size = 3) +
  labs(x = "placeholder", y = element_blank()) +
  scale_x_continuous("Effect Size (Hedges' g)", limits = c(-1.9, 5.2), breaks = c(-2, -1, 0, 1, 2, 3, 4, 5)) +
  ggtitle(expression(paste("Forest Plot for Studies on ", italic(f)[o], " Variability"))) +
  theme_bw()
forest_plot_F0V <- forest_plot_F0V + theme(plot.title = element_text(hjust = 0.5, size=15))
forest_plot_F0V
```


2: Task, Environment, Age, Language as Predictors
---------------

It's time to build the full models:

```{r}
baseline_te <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + Age_months + 
                    Language + Environment + Task + (1 | Language/id_site/measurement_num))

priors1 <- c(prior(normal(0, 2.5), class = Intercept),
             prior(normal(1, 1), class = sd),
             prior(normal(0, 1), class = b),
             prior(normal(0, 0.05), class = b, coef = "Age_months"),
             prior(gamma(2, 0.1), class = nu))

F0_task_environment_language_age_m <- 
  brm_multiple(
    baseline_te,
    save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "F0_task_environment_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))

# saveRDS(F0_task_environment_language_age_m, here::here("models", "replication", "F0_task_environment_language_age_m_rep.RDS"))

summary(F0_task_environment_language_age_m)
pp_check(F0_task_environment_language_age_m, ndraws = 100)
```

```{r}
#Plot estimates according to language:
c_eff <- conditional_effects(F0_task_environment_language_age_m)
F0_age_language_model_data <- c_eff$Language

#use only the raw data that were included in the model (and not excluded due to age not being there):
data_F0_plot <- data_F0_final %>%
  filter(Age_months > 0)

F0_age_language_model_data$Language <- reorder(F0_age_language_model_data$Language, F0_age_language_model_data$estimate__)
data_F0_plot$Language_order <- match(data_F0_plot$Language, F0_age_language_model_data$Language)
data_F0_plot$Language <- as.factor(reorder(data_F0_plot$Language, data_F0_plot$Language_order))

c_eff_plot_language_F0 <- ggplot() +
  geom_vline(xintercept = 0, color = "black", size = 0.3, linetype="dotted") +
  geom_point(aes(y = Language, x = estimate__), data = F0_age_language_model_data, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = Language, x = estimate__), data = F0_age_language_model_data, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = F0_age_language_model_data, color = "steelblue") +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  geom_point(aes(y = Language, x = Effect_Size, size = 1/ Effect_Size_se), data = data_F0_plot, color = "black", alpha = 0.1, 
             position = position_jitter(width = 0, height = 0.2), shape = 21, stroke = 1.1, fill = "grey40") +
  xlab("Effect Size (Hedges' g)") +
  ylab("Language") +
  ggtitle(expression(paste(italic(f)[o], " as a Function of Language"))) +
  theme_bw()
c_eff_plot_language_F0 <- c_eff_plot_language_F0 + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                         legend.position = "none")
c_eff_plot_language_F0

#Plot estimates according to age:
c_eff_F0 <- conditional_effects(F0_task_environment_language_age_m, effects = 'Age_months', spaghetti = T, ndraws = 100)
c_eff_plot_age_F0 <- plot(c_eff_F0,
                          mean = FALSE, 
                          points = F, 
                          point_args = c(alpha = 0.3, size = 2, show.legend = FALSE, width = 0.4), 
                          spaghetti_args = c(alpha = 1, size = 0.4), 
                          plot = FALSE)[[1]]
c_eff_plot_age_F0 <- c_eff_plot_age_F0 +
  geom_hline(aes(yintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  scale_y_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  geom_point(aes(y = Effect_Size, x = Age_months, size = 1/ Effect_Size_se), data = data_F0_final, color = "black", alpha = 0.1, 
             shape = 21, stroke = 1.1, fill = "grey40") +
  xlab("Mean Age in Months") +
  ylab("Effect Size (Hedges' g)") +
  ggtitle(expression(paste(italic(f)[o], " as a Function of Age"))) +
  geom_line(color = "#FC4E07", size = 1) +
  guides(color = guide_legend(override.aes = list(alpha = 0.5, size = 1))) +
  scale_x_continuous(limits = c(0, 37), breaks=c(0, 5, 10, 15, 20, 25, 30, 35)) +
  theme_bw()

c_eff_plot_age_F0 <- c_eff_plot_age_F0 + theme(plot.title = element_text(hjust = 0.5, size=15),
                                               legend.position = "none")
c_eff_plot_age_F0

#Plots of Task and Environment:
c_eff <- conditional_effects(F0_task_environment_language_age_m)
data_F0_plot_task <- c_eff$Task

c_eff_plot_task_F0 <- ggplot() +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = data_F0_plot_task, color = "steelblue", width = 0.62, size = 1.5) +
  geom_point(aes(y = Task, x = Effect_Size, size = 1/ Effect_Size_se), data = data_F0_final, color = "black", alpha = 0.1,
             position = position_jitter(width = 0, height = 0.3), shape = 21, stroke = 1.1, fill = "grey40") +
  geom_point(aes(y = effect1__, x = estimate__), data = data_F0_plot_task, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = data_F0_plot_task, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  xlab("Effect Size (Hedges' g)") +
  ylab("Task") +
  ggtitle(expression(paste(italic(f)[o], " as a Function of Task"))) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  coord_flip() +
  theme_bw()
c_eff_plot_task_F0 <- c_eff_plot_task_F0 + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                 legend.position = "none")
c_eff_plot_task_F0

#Plot for environment:
data_F0_plot_environment <- c_eff$Environment

c_eff_plot_environment_F0 <- ggplot() +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = data_F0_plot_environment, color = "steelblue", width = 0.62, size = 1.5) +
  geom_point(aes(y = Environment, x = Effect_Size, size = 1/ Effect_Size_se), data = data_F0_final, color = "black", alpha = 0.1,
             position = position_jitter(width = 0, height = 0.3), shape = 21, stroke = 1.1, fill = "grey40") +
  geom_point(aes(y = effect1__, x = estimate__), data = data_F0_plot_environment, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = data_F0_plot_environment, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  xlab("Effect Size (Hedges' g)") +
  ylab("Environment") +
  ggtitle(expression(paste(italic(f)[o], " as a Function of Environment"))) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  coord_flip() +
  theme_bw()
c_eff_plot_environment_F0 <- c_eff_plot_environment_F0 + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                               legend.position = "none")
c_eff_plot_environment_F0
```

```{r}
#same for VSA:
VSA_task_environment_language_age_m <- 
  brm_multiple(
    baseline_te,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "VSA_task_environment_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))

# saveRDS(VSA_task_environment_language_age_m, file = here("models","VSA_task_environment_language_age_m_rep.RDS"))

summary(VSA_task_environment_language_age_m)
pp_check(VSA_task_environment_language_age_m, ndraws = 100)
```






```{r}
#Plots of Task and Environment:
#Plot estimates according to language:
c_eff <- conditional_effects(VSA_task_environment_language_age_m)
VSA_age_language_model_data <- c_eff$Language

data_VSA_plot <- data_VSA_final %>%
  filter(Age_months > 0)

VSA_age_language_model_data$Language <- reorder(VSA_age_language_model_data$Language, VSA_age_language_model_data$estimate__)
data_VSA_plot$Language_order <- match(data_VSA_plot$Language, VSA_age_language_model_data$Language)
data_VSA_plot$Language <- as.factor(reorder(data_VSA_plot$Language, data_VSA_plot$Language_order))

c_eff_plot_language_VSA <- ggplot() +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  geom_point(aes(y = reorder(effect1__, estimate__), x = estimate__), data = VSA_age_language_model_data, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = VSA_age_language_model_data, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = VSA_age_language_model_data, color = "steelblue") +
  geom_point(aes(y = Language, x = Effect_Size, size = 1/ Effect_Size_se), data = data_VSA_plot, color = "black", alpha = 0.1, 
             position = position_jitter(width = 0, height = 0.2), shape = 21, stroke = 1.1, fill = "grey40") +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  xlab("Effect Size (Hedges' g)") +
  ylab("Language") +
  ggtitle('Vowel Space Area as a Function of Language') +
  theme_bw()
c_eff_plot_language_VSA <- c_eff_plot_language_VSA + 
  theme(plot.title = element_text(hjust = 0.5, size=15), 
        legend.position = "none")
c_eff_plot_language_VSA

#Plot estimates according to age:
c_eff <- conditional_effects(VSA_task_environment_language_age_m, effects = 'Age_months', spaghetti = T, ndraws = 150, points = T)
c_eff_plot_age_VSA <- plot(c_eff,
                           mean = FALSE, 
                           points = F, 
                           point_args = c(alpha = 0.8, size = 2, show.legend = FALSE, width = 0.3), 
                           spaghetti_args = c(alpha = 1, size = 0.4), 
                           plot = FALSE)[[1]]
c_eff_plot_age_VSA <- c_eff_plot_age_VSA +
  scale_y_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  geom_point(aes(y = Effect_Size, x = Age_months, size = 1/ Effect_Size_se), data = data_VSA_final, color = "black", alpha = 0.1, 
             shape = 21, stroke = 1.1, fill = "grey40") +
  xlab("Mean Age in Months") +
  ylab("Effect Size (Hedges' g)") +
  ggtitle('Vowel Space Area as a Function of Age') +
  geom_hline(aes(yintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  geom_line(color = "#FC4E07") +
  guides(color = guide_legend(override.aes = list(alpha = 0.5, size = 1))) +
  scale_x_continuous(breaks=c(0, 5, 10, 15, 20, 25, 30, 35, 40)) +
  theme_bw()

c_eff_plot_age_VSA <- c_eff_plot_age_VSA + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                 legend.position = "none")
c_eff_plot_age_VSA

#Same for Task:
c_eff <- conditional_effects(VSA_task_environment_language_age_m)
data_VSA_plot_task <- c_eff$Task

c_eff_plot_task_VSA <- ggplot() +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = data_VSA_plot_task, color = "steelblue", width = 0.62, size = 1.5) +
  geom_point(aes(y = Task, x = Effect_Size, size = 1/ Effect_Size_se), data = data_VSA_final, color = "black", alpha = 0.1,
             position = position_jitter(width = 0, height = 0.3), shape = 21, stroke = 1.1, fill = "grey40") +
  geom_point(aes(y = effect1__, x = estimate__), data = data_VSA_plot_task, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = data_VSA_plot_task, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlab("Effect Size (Hedges' g)") +
  ylab("Task") +
  ggtitle('Vowel Space Area as a Function of Task') +
  coord_flip() +
  theme_bw()
c_eff_plot_task_VSA <- c_eff_plot_task_VSA + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                   legend.position = "none")
c_eff_plot_task_VSA

#Plot for environment:
data_VSA_plot_environment <- c_eff$Environment

c_eff_plot_environment_VSA <- ggplot() +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = data_VSA_plot_environment, color = "steelblue", width = 0.62, size = 1.5) +
  geom_point(aes(y = Environment, x = Effect_Size, size = 1/ Effect_Size_se), data = data_VSA_final, color = "black", alpha = 0.1,
             position = position_jitter(width = 0, height = 0.3), shape = 21, stroke = 1.1, fill = "grey40") +
  geom_point(aes(y = effect1__, x = estimate__), data = data_VSA_plot_environment, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = data_VSA_plot_environment, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlab("Effect Size (Hedges' g)") +
  ylab("Environment") +
  ggtitle('Vowel Space Area as a Function of Environment') +
  coord_flip() +
  theme_bw()
c_eff_plot_environment_VSA <- c_eff_plot_environment_VSA + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                                 legend.position = "none")
c_eff_plot_environment_VSA
```


```{r}
baseline_e <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + Age_months + 
                   Language + Environment + (1 | Language/id_site/measurement_num))


#same for AR:
AR_task_environment_language_age_m <- 
  brm_multiple(
    baseline_e,
    save_pars = save_pars(all = TRUE),
    data = data_AR_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "AR_task_environment_language_age_m_rep"),
    sample_prior = T,
    iter = 10000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))

# saveRDS(AR_task_environment_language_age_m, here("models", "replication", "AR_environment_language_age_m_rep.rds"))

summary(AR_task_environment_language_age_m)
pp_check(AR_task_environment_language_age_m, ndraws = 100)
```

```{r}
#Plot estimates according to Language:
c_eff <- conditional_effects(AR_task_environment_language_age_m)
AR_age_language_model_data <- c_eff$Language

c_eff_plot_language_AR <- ggplot() +
  geom_point(aes(y = reorder(effect1__, estimate__), x = estimate__), data = AR_age_language_model_data, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = AR_age_language_model_data, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = AR_age_language_model_data, color = "steelblue") +
  #geom_jitter(aes(y = Language, x = Effect_Size), height = 0.1, data = data_AR_final, color = "grey40", size = 1.5, alpha = 0.8) +
  geom_point(aes(y = Language, x = Effect_Size, size = 1/ Effect_Size_se), data = data_AR_final, color = "black", alpha = 0.1, 
             position = position_jitter(width = 0, height = 0.2), shape = 21, stroke = 1.1, fill = "grey40") +
  scale_x_continuous(breaks=c(-5, -4, -3, -2, -1, 0, 1)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlab("Effect Size (Hedges' g)") +
  ylab("Language") +
  ggtitle('Articulation Rate as a Function of Language') +
  theme_bw()
c_eff_plot_language_AR <- c_eff_plot_language_AR + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                         legend.position = "none")
c_eff_plot_language_AR

#Plot estimates according to Age: 
c_eff <- conditional_effects(AR_task_environment_language_age_m, effects = 'Age_months', spaghetti = T, ndraws = 100)
c_eff_plot_age_AR <- plot(c_eff,
                          mean = FALSE, 
                          points = F, 
                          point_args = c(alpha = 0.8, size = 2, show.legend = FALSE, width = 0.3), 
                          spaghetti_args = c(alpha = 1, size = 0.4), 
                          plot = FALSE)[[1]]
c_eff_plot_age_AR <- c_eff_plot_age_AR +
  geom_point(aes(y = Effect_Size, x = Age_months, size = 1/ Effect_Size_se), data = data_AR_final, color = "black", alpha = 0.1, 
             shape = 21, stroke = 1.1, fill = "grey40") +
  xlab("Mean Age in Months") +
  ylab("Effect Size (Hedges' g)") +
  ggtitle('Articulation Rate as a Function of Age') +
  geom_line(color = "#FC4E07") +
  geom_hline(aes(yintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  guides(color = guide_legend(override.aes = list(alpha = 0.5, size = 1))) +
  theme_bw()

c_eff_plot_age_AR <- c_eff_plot_age_AR + theme(plot.title = element_text(hjust = 0.5, size=15),
                                               legend.position = "none")
c_eff_plot_age_AR

#Plots of Task and Environment:
AR_task_environment_language_age_m <- readRDS('models/AR_task_environment_language_age_m.rds')
c_eff <- conditional_effects(AR_task_environment_language_age_m)
data_AR_plot_task <- c_eff$Task

c_eff_plot_task_AR <- ggplot() +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = data_AR_plot_task, color = "steelblue", width = 0.62, size = 1.5) +
  geom_point(aes(y = Task, x = Effect_Size, size = 1/ Effect_Size_se), data = data_AR_final, color = "black", alpha = 0.1,
             position = position_jitter(width = 0, height = 0.3), shape = 21, stroke = 1.1, fill = "grey40") +
  geom_point(aes(y = effect1__, x = estimate__), data = data_AR_plot_task, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = data_AR_plot_task, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlab("Effect Size (Hedges' g)") +
  ylab("Task") +
  ggtitle('Articulation Rate as a Function of Task') +
  coord_flip() +
  theme_bw()
c_eff_plot_task_AR <- c_eff_plot_task_AR + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                 legend.position = "none")
c_eff_plot_task_AR

#Plot for environment:
AR_task_environment_language_age_m <- readRDS('models/AR_environment_language_age_m.rds')
c_eff <- conditional_effects(AR_task_environment_language_age_m)
data_AR_plot_environment <- c_eff$Environment

c_eff_plot_environment_AR <- ggplot() +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = data_AR_plot_environment, color = "steelblue", width = 0.62, size = 1.5) +
  geom_point(aes(y = Environment, x = Effect_Size, size = 1/ Effect_Size_se), data = data_AR_final, color = "black", alpha = 0.1,
             position = position_jitter(width = 0, height = 0.3), shape = 21, stroke = 1.1, fill = "grey40") +
  geom_point(aes(y = effect1__, x = estimate__), data = data_AR_plot_environment, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = data_AR_plot_environment, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlab("Effect Size (Hedges' g)") +
  ylab("Environment") +
  ggtitle('Articulation Rate as a Function of Environment') +
  coord_flip() +
  theme_bw()
c_eff_plot_environment_AR <- c_eff_plot_environment_AR + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                               legend.position = "none")
c_eff_plot_environment_AR
```

```{r}
#Same for VD:
VD_task_environment_language_age_m <- 
  brm_multiple(
    baseline_te,
    save_pars = save_pars(all = TRUE),
    data = data_VD_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "VD_task_environment_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))

# saveRDS(VD_task_environment_language_age_m, here("models", "replication", "VD_task_environment_language_age_m_rep.RDS"))

summary(VD_task_environment_language_age_m)
pp_check(VD_task_environment_language_age_m, ndraws = 100)
```

```{r}
#Plot estimates according to Language:
c_eff <- conditional_effects(VD_task_environment_language_age_m)
VD_age_language_model_data <- c_eff$Language

c_eff_plot_language_VD <- ggplot() +
  geom_point(aes(y = reorder(effect1__, estimate__), x = estimate__), data = VD_age_language_model_data, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = VD_age_language_model_data, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = VD_age_language_model_data, color = "steelblue") +
  geom_point(aes(y = Language, x = Effect_Size, size = 1/ Effect_Size_se), data = data_VD_final, color = "black", alpha = 0.1, 
             position = position_jitter(width = 0, height = 0.2), shape = 21, stroke = 1.1, fill = "grey40") +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlab("Effect Size (Hedges' g)") +
  ylab("Language") +
  ggtitle('Vowel Duration as a Function of Language') +
  theme_bw()
c_eff_plot_language_VD <- c_eff_plot_language_VD + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                         legend.position = "none")
c_eff_plot_language_VD

#Plot estimates according to Age: 
c_eff <- conditional_effects(VD_task_environment_language_age_m, effects = 'Age_months', spaghetti = T, ndraws = 100)
c_eff_plot_age_VD <- plot(c_eff,
                          mean = FALSE, 
                          points = T, 
                          point_args = c(alpha = 0.8, size = 2, show.legend = FALSE, width = 0.3), 
                          spaghetti_args = c(alpha = 1, size = 0.4), 
                          plot = FALSE)[[1]]
c_eff_plot_age_VD <- c_eff_plot_age_VD +
  geom_point(aes(y = Effect_Size, x = Age_months, size = 1/ Effect_Size_se), data = data_VD_final, color = "black", alpha = 0.1, 
             shape = 21, stroke = 1.1, fill = "grey40") +
  geom_hline(aes(yintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlab("Mean Age in Months") +
  ylab("Effect Size (Hedges' g)") +
  ggtitle('Vowel Duration as a Function of Age') +
  geom_line(color = "#FC4E07") +
  guides(color = guide_legend(override.aes = list(alpha = 0.5, size = 1))) +
  theme_bw()

c_eff_plot_age_VD <- c_eff_plot_age_VD + theme(plot.title = element_text(hjust = 0.5, size=15),
                                               legend.position = "none")
c_eff_plot_age_VD

#Plots of Task and Environment:
c_eff <- conditional_effects(VD_task_environment_language_age_m)
data_VD_plot_task <- c_eff$Task

c_eff_plot_task_VD <- ggplot() +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = data_VD_plot_task, color = "steelblue", width = 0.62, size = 1.5) +
  geom_point(aes(y = Task, x = Effect_Size, size = 1/ Effect_Size_se), data = data_VD_final, color = "black", alpha = 0.1,
             position = position_jitter(width = 0, height = 0.3), shape = 21, stroke = 1.1, fill = "grey40") +
  geom_point(aes(y = effect1__, x = estimate__), data = data_VD_plot_task, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = data_VD_plot_task, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlab("Effect Size (Hedges' g)") +
  ylab("Task") +
  ggtitle('Vowel Duration as a Function of Task') +
  coord_flip() +
  theme_bw()
c_eff_plot_task_VD <- c_eff_plot_task_VD + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                 legend.position = "none")
c_eff_plot_task_VD

#Plot for environment:
data_VD_plot_environment <- c_eff$Environment

c_eff_plot_environment_VD <- ggplot() +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = data_VD_plot_environment, color = "steelblue", width = 0.62, size = 1.5) +
  geom_point(aes(y = Environment, x = Effect_Size, size = 1/ Effect_Size_se), data = data_VD_final, color = "black", alpha = 0.1,
             position = position_jitter(width = 0, height = 0.3), shape = 21, stroke = 1.1, fill = "grey40") +
  geom_point(aes(y = effect1__, x = estimate__), data = data_VD_plot_environment, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = data_VD_plot_environment, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlab("Effect Size (Hedges' g)") +
  ylab("Environment") +
  ggtitle('Vowel Duration as a Function of Environment') +
  coord_flip() +
  theme_bw()
c_eff_plot_environment_VD <- c_eff_plot_environment_VD + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                               legend.position = "none")
c_eff_plot_environment_VD
```

```{r}
#Same for F0V:
F0V_task_environment_language_age_m <- 
  brm_multiple(
    baseline_te,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "F0V_task_environment_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))

# saveRDS(VD_task_environment_language_age_m, here("models", "replication", "F0V_task_environment_language_age_m_rep.RDS"))


summary(F0V_task_environment_language_age_m)
pp_check(F0V_task_environment_language_age_m, ndraws = 100)

```

```{r}
#Plot estimates according to Language:
c_eff <- conditional_effects(F0V_task_environment_language_age_m)
F0V_age_language_model_data <- c_eff$Language

data_F0V_plot <- data_F0V_final %>%
  filter(Age_months > 0)

F0V_age_language_model_data$Language <- reorder(F0V_age_language_model_data$Language, F0V_age_language_model_data$estimate__)
data_F0V_plot$Language_order <- match(data_F0V_plot$Language, F0V_age_language_model_data$Language)
data_F0V_plot$Language <- as.factor(reorder(data_F0V_plot$Language, data_F0V_plot$Language_order))

c_eff_plot_language_F0V <- ggplot() +
  geom_point(aes(y = reorder(effect1__, estimate__), x = estimate__), data = F0V_age_language_model_data, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = F0V_age_language_model_data, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = F0V_age_language_model_data, color = "steelblue") +
  geom_point(aes(y = Language, x = Effect_Size, size = 1/ Effect_Size_se), data = data_F0V_plot, color = "black", alpha = 0.1, position = position_jitter(width = 0, height = 0.2), shape = 21, stroke = 1.1, fill = "grey40") +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlab("Effect Size (Hedges' g)") +
  ylab("Language") +
  ggtitle(expression(paste(italic(f)[o], " Variability as a Function of Language"))) +
  theme_bw()
c_eff_plot_language_F0V <- c_eff_plot_language_F0V + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                           legend.position = "none")

c_eff_plot_language_F0V

#Plot estimates according to Age: 
c_eff <- conditional_effects(F0V_task_environment_language_age_m, effects = 'Age_months', spaghetti = T, ndraws = 150)
c_eff_plot_age_F0V <- plot(c_eff,
                           mean = FALSE, 
                           points = F, 
                           point_args = c(alpha = 0.8, size = 2, show.legend = FALSE, width = 0.3), 
                           spaghetti_args = c(alpha = 1, size = 0.4), 
                           plot = FALSE)[[1]]
c_eff_plot_age_F0V <- c_eff_plot_age_F0V +
  geom_point(aes(y = Effect_Size, x = Age_months, size = 1/ Effect_Size_se), data = data_F0V_final, color = "black", alpha = 0.1, 
             shape = 21, stroke = 1.1, fill = "grey40") +
  geom_hline(aes(yintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlim(c(0, 38)) +
  xlab("Mean Age in Months") +
  ylab("Effect Size (Hedges' g)") +
  ggtitle(expression(paste(italic(f)[o], " Variability as a Function of Age"))) +
  geom_line(color = "#FC4E07") +
  guides(color = guide_legend(override.aes = list(alpha = 0.5, size = 1))) +
  theme_bw()

c_eff_plot_age_F0V <- c_eff_plot_age_F0V + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                 legend.position = "none")
c_eff_plot_age_F0V

#Plots of Task and Environment:
c_eff <- conditional_effects(F0V_task_environment_language_age_m)

data_F0V_plot_task <- c_eff$Task

c_eff_plot_task_F0V <- ggplot() +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = data_F0V_plot_task, color = "steelblue", width = 0.62, size = 1.5) +
  geom_point(aes(y = Task, x = Effect_Size, size = 1/ Effect_Size_se), data = data_F0V_final, color = "black", alpha = 0.1,
             position = position_jitter(width = 0, height = 0.3), shape = 21, stroke = 1.1, fill = "grey40") +
  geom_point(aes(y = effect1__, x = estimate__), data = data_F0V_plot_task, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = data_F0V_plot_task, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlab("Effect Size (Hedges' g)") +
  ylab("Task") +
  ggtitle(expression(paste(italic(f)[o], " Variability as a Function of Task"))) +
  coord_flip() +
  theme_bw()
c_eff_plot_task_F0V <- c_eff_plot_task_F0V + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                   legend.position = "none")
c_eff_plot_task_F0V

#Plot for environment:
data_F0V_plot_environment <- c_eff$Environment

c_eff_plot_environment_F0V <- ggplot() +
  geom_errorbar(aes(y = effect1__, xmin = lower__, xmax = upper__), data = data_F0V_plot_environment, color = "steelblue", width = 0.62, size = 1.5) +
  geom_point(aes(y = Environment, x = Effect_Size, size = 1/ Effect_Size_se), data = data_F0V_final, color = "black", alpha = 0.1,
             position = position_jitter(width = 0, height = 0.3), shape = 21, stroke = 1.1, fill = "grey40") +
  geom_point(aes(y = effect1__, x = estimate__), data = data_F0V_plot_environment, color = "black", fill = "black", size = 4, alpha = 1, stroke = 0.5) +
  geom_point(aes(y = effect1__, x = estimate__), data = data_F0V_plot_environment, color = "#FC4E07", fill = "black", size = 3, alpha = 0.9, stroke = 0.5) +
  scale_x_continuous(breaks=c(-2, -1, 0, 1, 2, 3, 4, 5, 6)) +
  scale_colour_manual(labels = c('Language'), values = c("#FC4E07")) +
  geom_vline(aes(xintercept = 0), color = "black", size = 0.3, linetype="dotted") +
  xlab("Effect Size (Hedges' g)") +
  ylab("Environment") +
  ggtitle(expression(paste(italic(f)[o], " Variability as a Function of Environment"))) +
  coord_flip() +
  theme_bw()
c_eff_plot_environment_F0V <- c_eff_plot_environment_F0V + theme(plot.title = element_text(hjust = 0.5, size=15),
                                                                 legend.position = "none")
c_eff_plot_environment_F0V
```

3: Task, Age, Language as Predictors
---------------

```{r, eval = FALSE}

#Add models with only task and environment for each of the acoustic measures:
baseline_t <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + Age_months + 
                   Language + Task + (1 | Language/id_site/measurement_num))

F0_task_language_age_m <- 
  brm_multiple(
    baseline_t,
    save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "F0_task_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

summary(F0_task_language_age_m)
pp_check(F0_task_language_age_m, ndraws = 100)

VSA_task_language_age_m <- 
  brm_multiple(
    baseline_t,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "VSA_task_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

AR_task_language_age_m <- 
  brm(
    baseline_t,
    save_pars = save_pars(all = TRUE),
    data = data_AR_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "AR_task_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

VD_task_language_age_m <- 
  brm_multiple(
    baseline_t,
    save_pars = save_pars(all = TRUE),
    data = data_VD_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "VD_task_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

F0V_task_language_age_m <- 
  brm_multiple(
    baseline_t,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "F0V_task_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

# saveRDS(F0_task_language_age_m, here("models", "replication", "F0_task_language_age_m_rep.rds"))
# saveRDS(VSA_task_language_age_m, here("models", "replication", "VSA_task_language_age_m_rep.rds"))
# saveRDS(AR_task_language_age_m, here("models", "replication", "AR_task_language_age_m_rep.rds"))
# saveRDS(VD_task_language_age_m, here("models", "replication", "VD_task_language_age_m_rep.rds"))
# saveRDS(F0V_task_language_age_m, here("models", "replication", "F0V_task_language_age_m_rep.rds"))

```

4: Environment, Age, Language as Predictors
---------------

```{r, eval = FALSE}
#Plot for environment:
baseline_e <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + Age_months + 
                   Language + Environment + (1 | Language/id_site/measurement_num))

F0_environment_language_age_m <- 
  brm_multiple(
    baseline_e,
    save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "F0_environment_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))

VSA_environment_language_age_m <- 
  brm_multiple(
    baseline_e,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "VSA_environment_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))

AR_environment_language_age_m <- 
  brm_multiple(
    baseline_e,
    save_pars = save_pars(all = TRUE),
    data = data_AR_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "AR_environment_language_age_m_rep"),
    sample_prior = T,
    iter = 10000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))

VD_environment_language_age_m <- 
  brm_multiple(
    baseline_e,
    save_pars = save_pars(all = TRUE),
    data = data_VD_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "VD_environment_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))

F0V_environment_language_age_m <- 
  brm_multiple(
    baseline_e,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "F0V_environment_language_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.999,
      max_treedepth = 20 ))
```


5: Age, Language as Predictors
---------------

```{r, eval = FALSE}
baseline_f <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + 
                   Language + Age_months + (1 | Language/id_site/measurement_num))

F0_age_language_m <- 
  brm_multiple(
    baseline_f,
    save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "F0_age_language_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(F0_age_language_m, ndraws = 100)

VSA_age_language_m <- 
  brm_multiple(
    baseline_f,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "VSA_age_language_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(VSA_age_language_m, ndraws = 100)

AR_age_language_m <- 
  brm_multiple(
    baseline_f,
    save_pars = save_pars(all = TRUE),
    data = data_AR_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "AR_age_language_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(AR_age_language_m, ndraws = 100)

VD_age_language_m <- 
  brm_multiple(
    baseline_f,
    save_pars = save_pars(all = TRUE),
    data = data_VD_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "VD_age_language_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(VD_age_language_m, ndraws = 100)

F0V_age_language_m <- 
  brm_multiple(
    baseline_f,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_multiple_final,
    family = student,
    prior = priors1,
    file = here("models", "replication", "F0V_age_language_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(F0V_age_language_m, ndraws = 100)
```





6: Language as Predictors
---------------

```{r, eval = FALSE}
baseline_a <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + Language + (1 | Study/Language/measurement_num))

priors2 <- c(prior(normal(0, 2.5), class = Intercept),
             prior(normal(1, 1), class = sd),
             prior(normal(0, 1), class = b),
             prior(gamma(2, 0.1), class = nu))

F0_language_m <- 
  brm_multiple(
    baseline_a,
    save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "F0_language_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

VSA_language_m <- 
  brm_multiple(
    baseline_a,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "VSA_language_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

AR_language_m <- 
  brm_multiple(
    baseline_a,
    save_pars = save_pars(all = TRUE),
    data = data_AR_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "AR_language_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

VD_language_m <- 
  brm_multiple(
    baseline_a,
    save_pars = save_pars(all = TRUE),
    data = data_VD_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "VD_language_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(VD_language_m, ndraws = 50)

F0V_language_m <- 
  brm_multiple(
    baseline_a,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "F0V_language_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(F0V_language_m, ndraws = 50)
```



7: Age as Predictor
---------------

```{r, eval = FALSE, warning=FALSE}
baseline_o <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + Age_months + (1 | Language/id_site/measurement_num))

F0_age_m <- 
  brm_multiple(
    baseline_o,
    save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "F0_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

# pp_check(F0_age_m, ndraws = 50)

VSA_age_m <- 
  brm_multiple(
    baseline_o,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "VSA_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

# pp_check(VSA_age_m, ndraws = 50)

AR_age_m <- 
  brm_multiple(
    baseline_o,
    save_pars = save_pars(all = TRUE),
    data = data_AR_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "AR_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

# pp_check(AR_age_m, ndraws = 50)

VD_age_m <- 
  brm_multiple(
    baseline_o,
    save_pars = save_pars(all = TRUE),
    data = data_VD_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "VD_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

# pp_check(VD_age_m, ndraws = 50)

F0V_age_m <- 
  brm_multiple(
    baseline_o,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_multiple_final,
    family = student,
    prior = priors1,
    file = here("models", "replication", "F0V_age_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

# pp_check(F0V_age_m, ndraws = 50)
```



8: Compute Influence of Data Imputation
---------------

```{r, warning=FALSE}
data_F0 <- readRDS("data_F0_final.RData")
data_VSA <- readRDS("data_VSA_final.RData")
data_AR <- readRDS("data_AR_final.RData")
data_VD <- readRDS("data_VD_final.RData")
data_F0V <- readRDS("data_F0V_final.RData")

#We use only the data that report means and sds:
effectsize <- esc_mean_sd(grp2m = data_F0$F0_Mean_ADS,
                          grp2sd = data_F0$F0_Mean_ADS_SD,
                          grp2n = data_F0$Sample_Size_ADS,
                          grp1m = data_F0$F0_Mean_IDS,
                          grp1sd = data_F0$F0_Mean_IDS_SD,
                          grp1n = data_F0$Sample_Size_IDS, 
                          es.type = "g")

data_F0_nonimputed <- data_F0 %>%
  mutate(Effect_Size = effectsize$es) %>%
  mutate(Effect_Size_se = effectsize$se) %>%
  mutate(measurement_num = seq(1, nrow(data_F0))) %>%
  drop_na()

F0_intercept_nonimputed <- 
  brm(
    baseline_z,
    save_pars = save_pars(all = TRUE),
    data = data_F0_nonimputed, 
    family = student,
    prior = priors,
    file = here("models", "replication", "F0_intercept_nonimputed_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))
pp_check(F0_intercept_nonimputed, ndraws = 100)

F0_intercept_nonimputed
F0_intercept_m

#We use only the data that report means and sds:
effectsize <- esc_mean_sd(grp2m = data_VSA$VSA_ADS,
                          grp2sd = data_VSA$VSA_ADS_SD,
                          grp2n = data_VSA$Sample_Size_ADS,
                          grp1m = data_VSA$VSA_IDS,
                          grp1sd = data_VSA$VSA_IDS_SD,
                          grp1n = data_VSA$Sample_Size_IDS, 
                          es.type = "g")

data_VSA_nonimputed <- data_VSA %>%
  mutate(Effect_Size = effectsize$es) %>%
  mutate(Effect_Size_se = effectsize$se) %>%
  mutate(measurement_num = seq(1, nrow(data_VSA))) %>%
  drop_na()

VSA_intercept_nonimputed <- 
  brm(
    baseline_z,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_nonimputed, 
    family = student,
    prior = priors,
    file = here("models", "replication", "VSA_intercept_nonimputed_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = 2,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(VSA_intercept_nonimputed, ndraws = 100)
VSA_intercept_nonimputed
VSA_intercept_m

#We use only the data that report means and sds:
effectsize <- esc_mean_sd(grp2m = data_AR$Articulation_Rate_ADS,
                          grp2sd = data_AR$Articulation_Rate_ADS_SD,
                          grp2n = data_AR$Sample_Size_ADS,
                          grp1m = data_AR$Articulation_Rate_IDS,
                          grp1sd = data_AR$Articulation_Rate_IDS_SD,
                          grp1n = data_AR$Sample_Size_IDS, 
                          es.type = "g")

data_AR_nonimputed <- data_AR %>%
  mutate(Effect_Size = effectsize$es) %>%
  mutate(Effect_Size_se = effectsize$se) %>%
  mutate(measurement_num = seq(1, nrow(data_AR))) %>%
  drop_na()

AR_intercept_nonimputed <- 
  brm(
    baseline_z,
    save_pars = save_pars(all = TRUE),
    data = data_AR_nonimputed, 
    family = student,
    prior = priors,
    file = here("models", "replication", "AR_intercept_nonimputed_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(AR_intercept_nonimputed, ndraws = 100)
AR_intercept_nonimputed
AR_intercept_m

#same for vowel duration:
#We use only the data that report means and sds:
effectsize <- esc_mean_sd(grp2m = data_VD$ADS_Vowel_Duration,
                          grp2sd = data_VD$ADS_Vowel_Duration_SD,
                          grp2n = data_VD$Sample_Size_ADS,
                          grp1m = data_VD$IDS_Vowel_Duration,
                          grp1sd = data_VD$IDS_Vowel_Duration_SD,
                          grp1n = data_VD$Sample_Size_IDS, 
                          es.type = "g")

data_VD_nonimputed <- data_VD %>%
  mutate(Effect_Size = effectsize$es) %>%
  mutate(Effect_Size_se = effectsize$se) %>%
  mutate(measurement_num = seq(1, nrow(data_VD))) %>%
  drop_na()

VD_intercept_nonimputed <- 
  brm(
    baseline_z,
    save_pars = save_pars(all = TRUE),
    data = data_VD_nonimputed, 
    family = student,
    prior = priors,
    file = here("models", "replication", "VD_intercept_nonimputed_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = 2,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(VD_intercept_nonimputed, ndraws = 100)
VD_intercept_nonimputed
VD_intercept_m

#same for F0 variability:
#We use only the data that report means and sds:
effectsize <- esc_mean_sd(grp2m = data_F0V$ADS_F0_Variability,
                          grp2sd = data_F0V$ADS_F0_Variability_SD,
                          grp2n = data_F0V$Sample_Size_ADS,
                          grp1m = data_F0V$IDS_F0_Variability,
                          grp1sd = data_F0V$IDS_F0_Variability_SD,
                          grp1n = data_F0V$Sample_Size_IDS, 
                          es.type = "g")

data_F0V_nonimputed <- data_F0V %>%
  mutate(Effect_Size = effectsize$es) %>%
  mutate(Effect_Size_se = effectsize$se) %>%
  mutate(measurement_num = seq(1, nrow(data_F0V))) %>%
  drop_na()

F0V_intercept_nonimputed <- 
  brm(
    baseline_z,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_nonimputed, 
    family = student,
    prior = priors,
    file = here("models", "replication", "F0V_intercept_nonimputed_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(F0V_intercept_nonimputed, ndraws = 100)
F0V_intercept_nonimputed
```

9: Prior Predictive Models
---------------

```{r}
#Let's start with a prior predictive check:
F0_intercept_prior <- 
  brm(
    baseline_z,
    data = data_F0_multiple_final[[1]],
    family = student,
    prior = priors,
    sample_prior = "only",
    file = here("models", "replication", "F0_intercept_prior_rep"),
    #backend = "cmdstanr",
    #threads = threading(2),
    iter = 2000,
    warmup = 500,
    cores = 2,
    chains = 2,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 20))

#Let's start with a prior predictive check:
VSA_intercept_prior <- 
  brm(
    baseline_z,
    data = data_VSA_multiple_final[[1]],
    family = student,
    prior = priors,
    sample_prior = "only",
    file = here("models", "replication", "VSA_intercept_prior_rep"),
    #backend = "cmdstanr",
    #threads = threading(2),
    iter = 2000,
    warmup = 500,
    cores = 2,
    chains = 2,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 20))

#Let's start with a prior predictive check:
AR_intercept_prior <- 
  brm(
    baseline_z,
    data = data_AR_multiple_final[[1]],
    family = student,
    prior = priors,
    sample_prior = "only",
    file = here("models", "replication", "AR_intercept_prior_rep"),
    #backend = "cmdstanr",
    #threads = threading(2),
    iter = 2000,
    warmup = 500,
    cores = 2,
    chains = 2,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 20))

#Let's start with a prior predictive check:
VD_intercept_prior <- 
  brm(
    baseline_z,
    data = data_VD_multiple_final[[1]],
    family = student,
    prior = priors,
    sample_prior = "only",
    file = here("models", "replication",  "VD_intercept_prior_rep"),
    #backend = "cmdstanr",
    #threads = threading(2),
    iter = 2000,
    warmup = 500,
    cores = 2,
    chains = 2,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 20))

#Let's start with a prior predictive check:
F0V_intercept_prior <- 
  brm(
    baseline_z,
    data = data_F0V_multiple_final[[1]],
    family = student,
    prior = priors,
    sample_prior = "only",
    file = here("models", "replication", "F0V_intercept_prior_rep"),
    #backend = "cmdstanr",
    #threads = threading(2),
    iter = 2000,
    warmup = 500,
    cores = 2,
    chains = 2,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 20))

```

10: Analysis of Publication Bias
---------------

```{r, warning = FALSE}
#calculate severity of publication bias needed to "explain away" the results:
svalue_F0 <- svalue( yi = data_F0_final$Effect_Size,
                  vi = data_F0_final$Effect_Size_se,
                  q=0.4,
                  clustervar = data_F0_final$Study,
                  model = "robust",
                  alpha.select = 0.05,
                  eta.grid.hi = 5,
                  favor.positive = TRUE,
                  CI.level = 0.95,
                  small = TRUE,
                  return.worst.meta = T)
svalue_F0

#make sensitivity plot, as in Mathur & VanderWeele (2020):
eta.list = as.list( c(150, rev( seq(1,100,1) ) ) )
res.list = lapply( eta.list, function(x) {
  #cat("\n Working on eta = ", x)
  return( corrected_meta( yi = data_F0_final$Effect_Size,
                          vi = data_F0_final$Effect_Size_se,
                          eta = x,
                          model = "robust",
                          favor.positive = TRUE,
                          clustervar = data_F0_final$Study) )
}
)

# put results for each eta in a dataframe and plot:
res.df = as.data.frame(do.call("rbind", res.list ))
#plot the results:
Sensitivity_analysis_F0 <- ggplot(data = res.df, aes(x = eta, y = est)) + 
  geom_ribbon( data = res.df, aes(x = eta, ymin = lo, ymax = hi), fill = "steelblue", alpha = 0.7) +
  geom_line( lwd = 1.5) +
  xlab( 'Publication Probability for Significant Studies') +
  ylab('Effect Size Esimate' ) + 
  geom_hline(yintercept = 0.0, linetype = "dotted", color = "red", size = 0.7) +
  geom_hline(yintercept = svalue_F0$meta.worst$b.r, linetype = "dashed", color = "#FC4E07", size = 0.7) +
  scale_y_continuous(breaks=seq(0.3,3,0.1)) +
  ylim(c(-0.01, 1.6)) +
  scale_x_continuous(breaks=c(0, 20, 40, 60, 80, 100, 120, 140, 160)) +
  theme_bw()

Sensitivity_analysis_F0 <- Sensitivity_analysis_F0 + 
  ggtitle(expression(paste("Sensitivity Analysis for ", italic(f)[o]))) +
  theme(plot.title = element_text(hjust = 0.5, size=15))

#create a significance funnel plot to examine publication bias:
sig_fun_F0 <- significance_funnel( yi = data_F0_final$Effect_Size,
                                vi = data_F0_final$Effect_Size_se,
                                xmin = min(data_F0_final$Effect_Size),
                                xmax = max(data_F0_final$Effect_Size),
                                ymin = min(sqrt(data_F0_final$Effect_Size_se)) - 0.1,
                                ymax = max(sqrt(data_F0_final$Effect_Size_se)) + 0.1,
                                xlab = "Point Estimate of Effect Size",
                                ylab = "Standard error of Effect Size",
                                favor.positive = T,
                                alpha.select = 0.05)
sig_fun_F0 <- sig_fun_F0 + 
  scale_colour_manual(values = c("#FC4E07", "steelblue")) + 
  ggtitle(expression(paste("Significance Funnel Plot for ", italic(f)[o]))) +
  theme_bw()

sig_fun_F0 <- sig_fun_F0 +
  geom_point(aes(x=svalue_F0$meta.worst$b.r, y=min(sqrt(data_F0_final$Effect_Size_se)) - 0.07), size = 8, shape = 18, colour="black", show.legend = F) +
  geom_point(aes(x=1.47, y=min(sqrt(data_F0_final$Effect_Size_se)) - 0.07), size = 8, shape = 18, colour="steelblue", show.legend = F) +
  geom_hline(yintercept = min(sqrt(data_F0_final$Effect_Size_se)) - 0.07, linetype = "dashed") +
  theme(plot.title = element_text(hjust = 0.5, size=15),
        legend.position = "none")

data_VSA_final <- data_VSA_final %>%
  drop_na()

#Same for VSA:
svalue_VSA <- svalue( yi = data_VSA_final$Effect_Size,
                  vi = data_VSA_final$Effect_Size_se,
                  q=0.0,
                  clustervar = data_VSA_final$Study,
                  model = "robust",
                  alpha.select = 0.05,
                  eta.grid.hi = 5,
                  favor.positive = TRUE,
                  CI.level = 0.95,
                  small = TRUE,
                  return.worst.meta = T)
svalue_VSA

#make sensitivity plot, as in Mathur & VanderWeele (2020):
eta.list = as.list( c(150, rev( seq(1,100,1) ) ) )
res.list = lapply( eta.list, function(x) {
  #cat("\n Working on eta = ", x)
  return( corrected_meta( yi = data_VSA_final$Effect_Size,
                          vi = data_VSA_final$Effect_Size_se,
                          eta = x,
                          model = "robust",
                          favor.positive = TRUE,
                          clustervar = data_VSA_final$Study) )
}
)
# put results for each eta in a dataframe and plot:
res.df = as.data.frame(do.call("rbind", res.list ))
#plot the results:
Sensitivity_analysis_VSA <- ggplot(data = res.df, aes(x = eta, y = est)) + 
  geom_ribbon( data = res.df, aes(x = eta, ymin = lo, ymax = hi), fill = "steelblue", alpha = 0.7) +
  geom_line( lwd = 1.5) +
  xlab( 'Publication Probability for Significant Studies') +
  ylab('Effect Size Esimate' ) + 
  geom_hline(yintercept = 0.0, linetype = "dotted", color = "red", size = 0.7) +
  geom_hline(yintercept = svalue_VSA$meta.worst$b.r, linetype = "dashed", color = "#FC4E07", size = 0.7) +
  scale_y_continuous(breaks=seq(0,3,0.1)) +
  scale_x_continuous(breaks=c(0, 20, 40, 60, 80, 100, 120, 140, 160)) +
  theme_bw()

Sensitivity_analysis_VSA <- Sensitivity_analysis_VSA + ggtitle("Sensitivity Analysis for Vowel Space Area") +
  theme(plot.title = element_text(hjust = 0.5, size=15))

#create a significance funnel plot to examine publication bias:
sig_fun_VSA <- significance_funnel(yi = data_VSA_final$Effect_Size,
                                   vi = data_VSA_final$Effect_Size_se,
                                   xmin = min(data_VSA_final$Effect_Size),
                                   xmax = max(data_VSA_final$Effect_Size),
                                   ymin = min(sqrt(data_VSA_final$Effect_Size_se)) - 0.1,
                                   ymax = max(sqrt(data_VSA_final$Effect_Size_se)) + 0.1,
                                   xlab = "Point Estimate of Effect Size",
                                   ylab = "Standard error of Effect Size",
                                   favor.positive = T,
                                   alpha.select = 0.05)
sig_fun_VSA <- sig_fun_VSA + 
  scale_colour_manual(values = c("#FC4E07", "steelblue")) + 
  ggtitle("Significance Funnel Plot for Vowel Space Area") +
  theme_bw()

sig_fun_VSA <- sig_fun_VSA +
  geom_point(aes(x=svalue_VSA$meta.worst$b.r, y=min(sqrt(data_VSA_final$Effect_Size_se)) - 0.07), size = 8, shape = 18, colour="black", show.legend = F) +
  geom_point(aes(x=0.68, y=min(sqrt(data_VSA_final$Effect_Size_se)) - 0.07), size = 8, shape = 18, colour="steelblue", show.legend = F) +
  geom_hline(yintercept = min(sqrt(data_VSA_final$Effect_Size_se)) - 0.07, linetype = "dashed") +
  theme(plot.title = element_text(hjust = 0.5, size=15),
        legend.position = "none")

#Same for AR:
svalue_AR <- svalue( yi = data_AR_final$Effect_Size,
                      vi = data_AR_final$Effect_Size_se,
                      q= -0.2,
                      clustervar = data_AR_final$Study,
                      model = "robust",
                      alpha.select = 0.05,
                      eta.grid.hi = 5,
                      favor.positive = FALSE,
                      CI.level = 0.95,
                      small = TRUE,
                      return.worst.meta = T)
svalue_AR

#make sensitivity plot, as in Mathur & VanderWeele (2020):
eta.list = as.list( c(150, rev( seq(1,100,1) ) ) )
res.list = lapply( eta.list, function(x) {
  #cat("\n Working on eta = ", x)
  return( corrected_meta( yi = data_AR_final$Effect_Size,
                          vi = data_AR_final$Effect_Size_se,
                          eta = x,
                          model = "robust",
                          favor.positive = FALSE,
                          clustervar = data_AR_final$Study) )
}
)
# put results for each eta in a dataframe and plot:
res.df = as.data.frame(do.call("rbind", res.list ))
#plot the results:
Sensitivity_analysis_AR <- ggplot(data = res.df, aes(x = eta, y = est)) + 
  geom_ribbon( data = res.df, aes(x = eta, ymin = lo, ymax = hi), fill = "steelblue", alpha = 0.7) +
  geom_line( lwd = 1.5) +
  xlab( 'Publication Probability for Significant Studies') +
  ylab('Effect Size Esimate' ) + 
  geom_hline(yintercept = 0.0, linetype = "dotted", color = "red", size = 0.7) +
  geom_hline(yintercept = -svalue_AR$meta.worst$b.r, linetype = "dashed", color = "#FC4E07", size = 0.7) +
  scale_y_continuous(breaks=seq(-1,0, 0.1)) +
  scale_x_continuous(breaks=c(0, 20, 40, 60, 80, 100, 120, 140, 160)) +
  theme_bw()

Sensitivity_analysis_AR <- Sensitivity_analysis_AR + ggtitle("Sensitivity Analysis for Articulation Rate") +
  theme(plot.title = element_text(hjust = 0.5, size=15))

#create a significance funnel plot to examine publication bias:
sig_fun_AR <- significance_funnel(yi = data_AR_final$Effect_Size,
                                   vi = data_AR_final$Effect_Size_se,
                                   xmin = min(data_AR_final$Effect_Size),
                                   xmax = max(data_AR_final$Effect_Size),
                                   ymin = min(sqrt(data_AR_final$Effect_Size_se)) - 0.15,
                                   ymax = max(sqrt(data_AR_final$Effect_Size_se)) + 0.15,
                                   xlab = "Point Estimate of Effect Size",
                                   ylab = "Standard error of Effect Size",
                                   favor.positive = F,
                                   alpha.select = 0.05)
sig_fun_AR <- sig_fun_AR + 
  scale_colour_manual(values = c("#FC4E07", "steelblue")) + 
  ggtitle("Significance Funnel Plot for Articulation Rate") +
  theme_bw()

sig_fun_AR <- sig_fun_AR +
  geom_point(aes(x=-svalue_AR$meta.worst$b.r, y=min(sqrt(data_AR_final$Effect_Size_se)) - 0.1), size = 8, shape = 18, colour="black", show.legend = F) +
  geom_point(aes(x=-1.03, y=min(sqrt(data_AR_final$Effect_Size_se)) - 0.1), size = 8, shape = 18, colour="steelblue", show.legend = F) +
  geom_hline(yintercept = min(sqrt(data_AR_final$Effect_Size_se)) - 0.1, linetype = "dashed") +
  theme(plot.title = element_text(hjust = 0.5, size=15),
        legend.position = "none")

#Same for VD:
svalue_VD <- svalue( yi = data_VD_final$Effect_Size,
                      vi = data_VD_final$Effect_Size_se,
                      q=0.18,
                      clustervar = data_VD_final$Study,
                      model = "robust",
                      alpha.select = 0.05,
                      eta.grid.hi = 5,
                      favor.positive = TRUE,
                      CI.level = 0.95,
                      small = TRUE,
                      return.worst.meta = T)
svalue_VD

#make sensitivity plot, as in Mathur & VanderWeele (2020):
eta.list = as.list( c(150, rev( seq(1,100,1) ) ) )
res.list = lapply( eta.list, function(x) {
  #cat("\n Working on eta = ", x)
  return( corrected_meta( yi = data_VD_final$Effect_Size,
                          vi = data_VD_final$Effect_Size_se,
                          eta = x,
                          model = "robust",
                          favor.positive = TRUE,
                          clustervar = data_VD_final$Study) )
}
)
# put results for each eta in a dataframe and plot:
res.df = as.data.frame(do.call("rbind", res.list ))
#plot the results:
Sensitivity_analysis_VD <- ggplot(data = res.df, aes(x = eta, y = est)) + 
  geom_ribbon( data = res.df, aes(x = eta, ymin = lo, ymax = hi), fill = "steelblue", alpha = 0.7) +
  geom_line( lwd = 1.5) +
  xlab( 'Publication Probability for Significant Studies') +
  ylab('Effect Size Esimate' ) + 
  geom_hline(yintercept = 0.0, linetype = "dotted", color = "red", size = 0.7) +
  geom_hline(yintercept = svalue_VD$meta.worst$b.r, linetype = "dashed", color = "#FC4E07", size = 0.7) +
  scale_y_continuous(breaks=seq(0,3,0.1)) +
  scale_x_continuous(breaks=c(0, 20, 40, 60, 80, 100, 120, 140, 160)) +
  theme_bw()

Sensitivity_analysis_VD <- Sensitivity_analysis_VD + ggtitle("Sensitivity Analysis for Vowel Duration") +
  theme(plot.title = element_text(hjust = 0.5, size=15))

#create a significance funnel plot to examine publication bias:
sig_fun_VD <- significance_funnel(yi = data_VD_final$Effect_Size,
                                   vi = data_VD_final$Effect_Size_se,
                                   xmin = min(data_VD_final$Effect_Size),
                                   xmax = max(data_VD_final$Effect_Size),
                                   ymin = min(sqrt(data_VD_final$Effect_Size_se)) - 0.15,
                                   ymax = max(sqrt(data_VD_final$Effect_Size_se)) + 0.15,
                                   xlab = "Point Estimate of Effect Size",
                                   ylab = "Standard error of Effect Size",
                                   favor.positive = T,
                                   alpha.select = 0.05)
sig_fun_VD <- sig_fun_VD + 
  scale_colour_manual(values = c("#FC4E07", "steelblue")) + 
  ggtitle("Significance Funnel Plot for Vowel Duration") +
  theme_bw()

sig_fun_VD <- sig_fun_VD +
  geom_point(aes(x=svalue_VD$meta.worst$b.r, y=min(sqrt(data_VD_final$Effect_Size_se)) - 0.1), size = 8, shape = 18, colour="black", show.legend = F) +
  geom_point(aes(x=0.57, y=min(sqrt(data_VD_final$Effect_Size_se)) - 0.1), size = 8, shape = 18, colour="steelblue", show.legend = F) +
  geom_hline(yintercept = min(sqrt(data_VD_final$Effect_Size_se)) - 0.1, linetype = "dashed") +
  theme(plot.title = element_text(hjust = 0.5, size=15),
        legend.position = "none")

#Same for F0V:
svalue_F0V <- svalue( yi = data_F0V_final$Effect_Size,
                     vi = data_F0V_final$Effect_Size_se,
                     q=0.2,
                     clustervar = data_F0V_final$Study,
                     model = "robust",
                     alpha.select = 0.05,
                     eta.grid.hi = 5,
                     favor.positive = TRUE,
                     CI.level = 0.95,
                     small = TRUE,
                     return.worst.meta = T)


#make sensitivity plot, as in Mathur & VanderWeele (2020):
eta.list = as.list( c(150, rev( seq(1,100,1) ) ) )
res.list = lapply( eta.list, function(x) {
  #cat("\n Working on eta = ", x)
  return( corrected_meta( yi = data_F0V_final$Effect_Size,
                          vi = data_F0V_final$Effect_Size_se,
                          eta = x,
                          model = "robust",
                          favor.positive = TRUE,
                          clustervar = data_F0V_final$Study) )
}
)
# put results for each eta in a dataframe and plot:
res.df = as.data.frame(do.call("rbind", res.list ))
#plot the results:
Sensitivity_analysis_F0V <- ggplot(data = res.df, aes(x = eta, y = est)) + 
  geom_ribbon( data = res.df, aes(x = eta, ymin = lo, ymax = hi), fill = "steelblue", alpha = 0.7) +
  geom_line( lwd = 1.5) +
  xlab( 'Publication Probability for Significant Studies') +
  ylab('Effect Size Esimate' ) + 
  geom_hline(yintercept = 0.0, linetype = "dotted", color = "red", size = 0.7) +
  geom_hline(yintercept = svalue_F0V$meta.worst$b.r, linetype = "dashed", color = "#FC4E07", size = 0.7) +
  scale_y_continuous(breaks=seq(0,3,0.1)) +
  scale_x_continuous(breaks=c(0, 20, 40, 60, 80, 100, 120, 140, 160)) +
  theme_bw()

Sensitivity_analysis_F0V <- Sensitivity_analysis_F0V + 
  ggtitle(expression(paste("Sensitivity Analysis for ", italic(f)[o], " Variability"))) +
  theme(plot.title = element_text(hjust = 0.5, size=15))

#create a significance funnel plot to examine publication bias:
sig_fun_F0V <- significance_funnel(yi = data_F0V_final$Effect_Size,
                                  vi = data_F0V_final$Effect_Size_se,
                                  xmin = min(data_F0V_final$Effect_Size),
                                  xmax = max(data_F0V_final$Effect_Size),
                                  ymin = min(sqrt(data_F0V_final$Effect_Size_se)) - 0.1,
                                  ymax = max(sqrt(data_F0V_final$Effect_Size_se)) + 0.15,
                                  xlab = "Point Estimate of Effect Size",
                                  ylab = "Standard error of Effect Size",
                                  favor.positive = T,
                                  alpha.select = 0.05)
sig_fun_F0V <- sig_fun_F0V + 
  scale_colour_manual(values = c("#FC4E07", "steelblue")) + 
  ggtitle(expression(paste("Significance Funnel Plot for ", italic(f)[o], " Variability"))) +
  theme_bw()

sig_fun_F0V <- sig_fun_F0V +
  geom_point(aes(x=svalue_F0V$meta.worst$b.r, y=min(sqrt(data_F0V_final$Effect_Size_se)) - 0.1), size = 8, shape = 18, colour="black", show.legend = F) +
  geom_point(aes(x=0.95, y=min(sqrt(data_F0V_final$Effect_Size_se)) - 0.1), size = 8, shape = 18, colour="steelblue", show.legend = F) +
  geom_hline(yintercept = min(sqrt(data_F0V_final$Effect_Size_se)) - 0.1, linetype = "dashed") +
  theme(plot.title = element_text(hjust = 0.5, size=15),
        legend.position = "none")

#Plots of publication bias:
sig_fun_plot_all <- plot_grid(sig_fun_F0,
                              sig_fun_F0V,
                              sig_fun_VSA,
                              sig_fun_AR,
                              sig_fun_VD,
                              ncol = 2)

#Plots of publication bias:
sens_plot_all <- plot_grid(Sensitivity_analysis_F0,
                           Sensitivity_analysis_F0V,
                           Sensitivity_analysis_VSA,
                           Sensitivity_analysis_AR,
                           Sensitivity_analysis_VD,
                           ncol = 2)
```

11: Visualisation Panels
---------------

```{r}
#F0:
F0_conditional_effects <- plot_grid(c_eff_plot_age_F0, c_eff_plot_task_F0, c_eff_plot_environment_F0, ncol = 1)
c_eff_plot_F0 <- plot_grid(c_eff_plot_language_F0, F0_conditional_effects, ncol = 2)
c_eff_plot_F0

# BS: Added for reproduction
ggsave("~/ids-meta-replication/figures/c_eff_plot_F0.pdf", c_eff_plot_F0,
       height = 9, width = 9)

#VSA:
VSA_conditional_effects <- plot_grid(c_eff_plot_age_VSA, c_eff_plot_task_VSA, c_eff_plot_environment_VSA, ncol = 1)
c_eff_plot_VSA <- plot_grid(c_eff_plot_language_VSA, VSA_conditional_effects, ncol = 2)
c_eff_plot_VSA

# BS: Added for reproduction
ggsave("~/ids-meta-replication/figures/c_eff_plot_VSA.pdf", c_eff_plot_VSA,
       height = 9, width = 9)

#AR:
AR_conditional_effects <- plot_grid(c_eff_plot_age_AR, c_eff_plot_task_AR, c_eff_plot_environment_AR, ncol = 1)
c_eff_plot_AR <- plot_grid(c_eff_plot_language_AR, AR_conditional_effects, ncol = 2)
c_eff_plot_AR

# BS: Added for reproduction
ggsave("~/ids-meta-replication/figures/c_eff_plot_AR.pdf", c_eff_plot_AR,
       height = 9, width = 9)

#VD:
VD_conditional_effects <- plot_grid(c_eff_plot_age_VD, c_eff_plot_task_VD, c_eff_plot_environment_VD, ncol = 1)
c_eff_plot_VD <- plot_grid(c_eff_plot_language_VD, VD_conditional_effects, ncol = 2)
c_eff_plot_VD

# BS: Added for reproduction
ggsave("~/ids-meta-replication/figures/c_eff_plot_VD.pdf", c_eff_plot_VD,
       height = 9, width = 9)

#F0 Variability:
F0V_conditional_effects <- plot_grid(c_eff_plot_age_F0V, c_eff_plot_task_F0V, c_eff_plot_environment_F0V, ncol = 1)
c_eff_plot_F0V <- plot_grid(c_eff_plot_language_F0V, F0V_conditional_effects, ncol = 2)
c_eff_plot_F0V

# BS: Added for reproduction
ggsave("~/ids-meta-replication/figures/c_eff_plot_F0V.pdf", c_eff_plot_F0V,
       height = 9, width = 9)

#Overview of age plots, Figure S6.6:
c_eff_plot_age_F0_overview <- c_eff_plot_age_F0 +
  xlim(c(0, 37))

c_eff_plot_age_VSA_overview <- c_eff_plot_age_VSA +
  xlim(c(0, 37))

c_eff_plot_age_AR_overview <- c_eff_plot_age_AR +
  xlim(c(0, 37))

c_eff_plot_age_VD_overview <- c_eff_plot_age_VD +
  xlim(c(0, 37))

c_eff_plot_age_F0V_overview <- c_eff_plot_age_F0V +
  xlim(c(0, 37))

age_plot_overview <- plot_grid(c_eff_plot_age_F0_overview, 
                               c_eff_plot_age_F0V_overview, 
                               c_eff_plot_age_VSA_overview, 
                               c_eff_plot_age_AR_overview, 
                               c_eff_plot_age_VD_overview, 
                               ncol = 1)
age_plot_overview
```

12: Prior Predictive Checks
---------------

```{r}
F0_intercept_prior_pp_plot <- pp_check(F0_intercept_prior, ndraws = 50) +
  scale_color_manual(values = c('black', 'grey')) + 
  ggtitle(expression(paste("Prior Predictive Check for ", italic(f)[o]))) +
  theme(plot.title = element_text(hjust = 0.5, size = 15), 
        legend.title = element_blank())

F0_intercept_posterior_pp_plot <- pp_check(F0_intercept_m, ndraws = 50) +
  scale_color_manual(values = c('black', 'grey')) + 
  ggtitle(expression(paste("Posterior Predictive Check for ", italic(f)[o]))) +
  theme(plot.title = element_text(hjust = 0.5, size = 15), 
        legend.title = element_blank())

#pp checks for the models:
VSA_intercept_prior_pp_plot <- pp_check(VSA_intercept_prior, ndraws = 50) +
  scale_color_manual(values = c('black', 'grey')) + 
  ggtitle('Prior Predictive Check for Vowel Space Area') + 
  theme(plot.title = element_text(hjust = 0.5, size = 15), 
        legend.title = element_blank())

VSA_intercept_posterior_pp_plot <- pp_check(VSA_intercept_m, ndraws = 50) +
  scale_color_manual(values = c('black', 'grey')) + 
  ggtitle('Posterior Predictive Check for Vowel Space Area') + 
  theme(plot.title = element_text(hjust = 0.5, size = 15), 
        legend.title = element_blank())

#pp checks for the models:
AR_intercept_prior_pp_plot <- pp_check(AR_intercept_prior, ndraws = 50) +
  scale_color_manual(values = c('black', 'grey')) + 
  ggtitle('Prior Predictive Check for Articulation Rate') + 
  theme(plot.title = element_text(hjust = 0.5, size = 15), 
        legend.title = element_blank())

AR_intercept_posterior_pp_plot <- pp_check(AR_intercept_m, ndraws = 50) +
  scale_color_manual(values = c('black', 'grey')) + 
  ggtitle('Posterior Predictive Check for Articulation Rate') + 
  theme(plot.title = element_text(hjust = 0.5, size = 12), 
        legend.title = element_blank())

#pp checks for the models:
VD_intercept_prior_pp_plot <- pp_check(VD_intercept_prior, ndraws = 50) +
  scale_color_manual(values = c('black', 'grey')) + 
  ggtitle('Prior Predictive Check for Vowel Duration') + 
  theme(plot.title = element_text(hjust = 0.5, size = 15), 
        legend.title = element_blank())

VD_intercept_posterior_pp_plot <- pp_check(VD_intercept_m, ndraws = 50) +
  scale_color_manual(values = c('black', 'grey')) + 
  ggtitle('Posterior Predictive Check for Vowel Duration') + 
  theme(plot.title = element_text(hjust = 0.5, size = 15), 
        legend.title = element_blank())

#pp checks for the models:
F0V_intercept_prior_pp_plot <- pp_check(F0V_intercept_prior, ndraws = 50) +
  scale_color_manual(values = c('black', 'grey')) + 
  ggtitle(expression(paste("Prior Predictive Check for ", italic(f)[o], " Variability"))) +
  theme(plot.title = element_text(hjust = 0.5, size = 15), legend.title = element_blank())

F0V_intercept_posterior_pp_plot <- pp_check(F0V_intercept_m, ndraws = 50) +
  scale_color_manual(values = c('black', 'grey')) + 
  ggtitle(expression(paste("Posterior Predictive Check for ", italic(f)[o], " Variability"))) +
  theme(plot.title = element_text(hjust = 0.5, size = 15), legend.title = element_blank())

pp_checks_all <- plot_grid(F0_intercept_prior_pp_plot,
                           F0_intercept_posterior_pp_plot,
                           F0V_intercept_prior_pp_plot,
                           F0V_intercept_posterior_pp_plot,
                           VSA_intercept_prior_pp_plot,
                           VSA_intercept_posterior_pp_plot,
                           AR_intercept_prior_pp_plot,
                           AR_intercept_posterior_pp_plot,
                           VD_intercept_prior_pp_plot,
                           VD_intercept_posterior_pp_plot,
                           ncol = 2)
pp_checks_all
```

13: Age Distribution for Language and Measure
---------------

```{r}
#Plot to show age distributions for each language and measure:
age_distr_lang_F0 <- 
  ggplot() +
  geom_point(aes(y = reorder(Language, desc(Language)), x = Age_months), 
             data = data_F0_final, 
             color = "black", 
             fill = "black", 
             size = 3, 
             alpha = 1, 
             stroke = 0.5) +
  geom_point(aes(y = reorder(Language, desc(Language)), x = Age_months), 
             data = data_F0_final, 
             color = "#FC4E07", 
             fill = "black", 
             size = 2, 
             alpha = 0.9, 
             stroke = 0.5) +
  xlim(c(-0.2, 38)) +
  ylab('Language') +
  xlab('Infant Age in Months') +
  ggtitle(expression(paste("Age and Language Distribution for ", italic(f)[o]))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))


age_distr_lang_VSA <- 
  ggplot() +
  geom_point(aes(y = reorder(Language, desc(Language)), x = Age_months), 
             data = data_VSA_final, 
             color = "black", 
             fill = "black", 
             size = 3, 
             alpha = 1, 
             stroke = 0.5) +
  geom_point(aes(y = reorder(Language, desc(Language)), x = Age_months), 
             data = data_VSA_final, 
             color = "#FC4E07", 
             fill = "black", 
             size = 2, 
             alpha = 0.9, 
             stroke = 0.5) +
  xlim(c(-0.5, 28)) +
  ylab('Language') +
  xlab('Infant Age in Months') +
  ggtitle('Age and Language Distribution for Vowel Space Area') +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))


age_distr_lang_AR <- 
  ggplot() +
  geom_point(aes(y = reorder(Language, desc(Language)), x = Age_months), 
             data = data_AR_final, 
             color = "black", 
             fill = "black", 
             size = 3, 
             alpha = 1, 
             stroke = 0.5) +
  geom_point(aes(y = reorder(Language, desc(Language)), x = Age_months), 
             data = data_AR_final, 
             color = "#FC4E07", 
             fill = "black", 
             size = 2, 
             alpha = 0.9, 
             stroke = 0.5) +
  xlim(c(-0.5, 28)) +
  ylab('Language') +
  xlab('Infant Age in Months') +
  ggtitle('Age and Language Distribution for Articulation Rate') +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))


age_distr_lang_VD <- 
  ggplot() +
  geom_point(aes(y = reorder(Language, desc(Language)), x = Age_months), 
             data = data_VD_final, 
             color = "black", 
             fill = "black", 
             size = 3, 
             alpha = 1, 
             stroke = 0.5) +
  geom_point(aes(y = reorder(Language, desc(Language)), x = Age_months), 
             data = data_VD_final, 
             color = "#FC4E07", 
             fill = "black", 
             size = 2, 
             alpha = 0.9, 
             stroke = 0.5) +
  xlim(c(-0.5, 28)) +
  ylab('Language') +
  xlab('Infant Age in Months') +
  ggtitle('Age and Language Distribution for Vowel Duration') +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))


age_distr_lang_F0V <- 
  ggplot() +
  geom_point(aes(y = reorder(Language, desc(Language)), x = Age_months), 
             data = data_F0V_final, 
             color = "black", 
             fill = "black", 
             size = 3, 
             alpha = 1, 
             stroke = 0.5) +
  geom_point(aes(y = reorder(Language, desc(Language)), x = Age_months), 
             data = data_F0V_final, 
             color = "#FC4E07", 
             fill = "black", 
             size = 2, 
             alpha = 0.9, 
             stroke = 0.5) +
  xlim(c(-0.5, 38)) +
  ylab('Language') +
  xlab('Infant Age in Months') +
  ggtitle(expression(paste("Age and Language Distribution for ", 
                           italic(f)[o], " Variability"))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))

age_distr_lang_all <- plot_grid(age_distr_lang_F0,
                                age_distr_lang_F0V,
                                age_distr_lang_VSA,
                                age_distr_lang_AR,
                                age_distr_lang_VD,
                                ncol = 2)
age_distr_lang_all
```

14: Cross-Tab for Task and Environment
---------------

```{r}
#Make cross-tab for task and environment:
cross_tab_task_environment_F0 <- ggplot(aes(y = Task, 
                   x = Age_months, 
                   color = Environment), 
               data = data_F0_final) + 
  labs(y= "Task", x = "Infant Age in Months") + 
  scale_colour_manual(values = c("#FC4E07", "steelblue")) +
  ggtitle(expression(paste("Cross-Tab for ", italic(f)[o]))) +
  geom_jitter(aes(color = Environment), height = 0.3, alpha = 0.7, size = 3) +
  facet_grid(~Environment, scales = "fixed") +
  theme_bw()
cross_tab_task_environment_F0 <- cross_tab_task_environment_F0 + theme(plot.title = element_text(hjust = 0.5, size=15),
             strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
             strip.text.x = element_text(size = 10, color = "black"),
             axis.text.y = element_text(size = 10, color = "black"),
             legend.position = "none")

cross_tab_task_environment_VSA <- ggplot(aes(y = Task, 
                   x = Age_months, 
                   color = Environment), 
               data = data_VSA_final) + 
  labs(y= "Task", x = "Infant Age in Months") + 
  scale_colour_manual(values = c("#FC4E07", "steelblue")) +
  ggtitle('Cross-Tab for Vowel Space Area') +
  geom_jitter(aes(color = Environment), height = 0.3, alpha = 0.7, size = 3) +
  facet_grid(~Environment, scales = "fixed") +
  theme_bw()
cross_tab_task_environment_VSA <- cross_tab_task_environment_VSA + theme(plot.title = element_text(hjust = 0.5, size=15),
             strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
             strip.text.x = element_text(size = 10, color = "black"),
             axis.text.y = element_text(size = 10, color = "black"),
             legend.position = "none")

cross_tab_task_environment_AR <- ggplot(aes(y = Task, 
                   x = Age_months, 
                   color = Environment), 
               data = data_AR_final) + 
  labs(y= "Task", x = "Infant Age in Months") + 
  scale_colour_manual(values = c("#FC4E07", "steelblue")) +
  ggtitle('Cross-Tab for Articulation Rate') +
  geom_jitter(aes(color = Environment), height = 0.3, alpha = 0.7, size = 3) +
  facet_grid(~Environment, scales = "fixed") +
  theme_bw()
cross_tab_task_environment_AR <- cross_tab_task_environment_AR + theme(plot.title = element_text(hjust = 0.5, size=15),
             strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
             strip.text.x = element_text(size = 10, color = "black"),
             axis.text.y = element_text(size = 10, color = "black"),
             legend.position = "none")

cross_tab_task_environment_VD <- ggplot(aes(y = Task, 
                   x = Age_months, 
                   color = Environment), 
               data = data_VD_final) + 
  labs(y= "Task", x = "Infant Age in Months") + 
  scale_colour_manual(values = c("#FC4E07", "steelblue")) +
  ggtitle('Cross-Tab for Vowel Duration') +
  geom_jitter(aes(color = Environment), height = 0.3, alpha = 0.7, size = 3) +
  facet_grid(~Environment, scales = "fixed") +
  theme_bw()
cross_tab_task_environment_VD <- cross_tab_task_environment_VD + theme(plot.title = element_text(hjust = 0.5, size=15),
             strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
             strip.text.x = element_text(size = 10, color = "black"),
             axis.text.y = element_text(size = 10, color = "black"),
             legend.position = "none")

cross_tab_task_environment_F0V <- ggplot(aes(y = Task, 
           x = Age_months, 
           color = Environment), 
       data = data_F0V_final) + 
  labs(y= "Task", x = "Infant Age in Months") + 
  scale_colour_manual(values = c("#FC4E07", "steelblue")) +
  ggtitle(expression(paste("Cross-Tab for ", italic(f)[o], " Variability"))) +
  geom_jitter(aes(color = Environment), height = 0.3, alpha = 0.7, size = 3) +
  facet_grid(~Environment, scales = "fixed") +
  theme_bw()
cross_tab_task_environment_F0V <- cross_tab_task_environment_F0V + theme(plot.title = element_text(hjust = 0.5, size=15),
             strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
             strip.text.x = element_text(size = 10, color = "black"),
             axis.text.y = element_text(size = 10, color = "black"),
             legend.position = "none")

cross_tab_task_environment_all <- plot_grid(cross_tab_task_environment_F0,
                                            cross_tab_task_environment_F0V,
                                            cross_tab_task_environment_VSA,
                                            cross_tab_task_environment_AR,
                                            cross_tab_task_environment_VD,
                                            ncol = 2)
cross_tab_task_environment_all
```

15: Prior-Posterior Update Plots
---------------

```{r}
#PP Update Plots:
# Check prior-posterior update plots
Posterior <- as_draws_df(F0_task_environment_language_age_m)

F0_intercept_pp_update <- 
  ggplot(Posterior) +
  geom_density(aes(b_Intercept), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(prior_Intercept), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Intercept') +
  ggtitle(expression(paste("Prior-Posterior Update Plots for ", italic(f)[o]))) +
  theme_classic() + theme(plot.title = element_text(hjust = 0.5, size=15))

F0_nu_pp_update <- ggplot(Posterior) +
  geom_density(aes(nu), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(prior_nu), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Nu') +
  theme_classic()

F0_sd_pp_update <- ggplot(Posterior) +
  geom_density(aes(sd_Language__Intercept), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(prior_sd_Language), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Standard Deviation of Studies') +
  theme_classic()

F0_language_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_LanguageBislama), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(b_LanguageBritishEnglish), fill="#E41A1C", color="#E41A1C",alpha=0.4) + 
  geom_density(aes(b_LanguageCanadianEnglish), fill="#984EA3", color="#984EA3",alpha=0.4) + 
  geom_density(aes(b_LanguageDanish), fill="#7570B3", color="#7570B3",alpha=0.4) + 
  geom_density(aes(b_LanguageGerman), fill="#666666", color="#666666",alpha=0.4) + 
  geom_density(aes(b_LanguageDutch), fill="#66A61E" , color="#66A61E" ,alpha=0.4) + 
  geom_density(aes(b_LanguageFrench), fill="#FFFF33", color="#FFFF33",alpha=0.4) + 
  geom_density(aes(b_LanguageItalian), fill="#A65628", color="#A65628",alpha=0.4) + 
  geom_density(aes(prior_b_LanguageUSEnglish), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Slope, Language Estimates') +
  theme_classic()

F0_task_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_Taskspontaneousspeech), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(b_Environmentnaturalistic), fill="#A65628", color="#A65628",alpha=0.4) + 
  geom_density(aes(prior_b_Taskspontaneousspeech), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Slope, Task & Environment Estimates') +
  theme_classic()

F0_age_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_Age_months), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(prior_b_Age_months), fill="steelblue", color="steelblue",alpha=0.7) +
  xlab('Slope, Age Estimate') +
  theme_classic()

F0_pp_update <- plot_grid(F0_intercept_pp_update, 
                                       F0_language_pp_update, 
                                       F0_task_pp_update, 
                                       F0_age_pp_update, 
                                       F0_sd_pp_update, 
                                       F0_nu_pp_update,
                                       ncol = 1)
F0_pp_update
# Check prior-posterior update plots
#variables(VSA_task_environment_language_age_m)
Posterior <- as_draws_df(VSA_task_environment_language_age_m)

VSA_intercept_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_Intercept), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(prior_Intercept), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Intercept') +
  ggtitle('Prior-Posterior Update Plots for Vowel Space Area') +
  theme_classic() + theme(plot.title = element_text(hjust = 0.5, size=15))

VSA_nu_pp_update <- ggplot(Posterior) +
  geom_density(aes(nu), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(prior_nu), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Nu') +
  theme_classic()

VSA_sd_pp_update <- ggplot(Posterior) +
  geom_density(aes(sd_Language__Intercept), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(prior_sd_Language), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Standard Deviation of Studies') +
  theme_classic()

VSA_language_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_LanguageBritishEnglish), fill="#E41A1C", color="#E41A1C",alpha=0.4) + 
  geom_density(aes(b_LanguageDanish), fill="#7570B3", color="#7570B3",alpha=0.4) + 
  geom_density(aes(b_LanguageFrench), fill="#FFFF33", color="#FFFF33",alpha=0.4) + 
  geom_density(aes(b_LanguageCantoneseChinese), fill="#A65628", color="#A65628",alpha=0.4) + 
  geom_density(aes(prior_b_LanguageUSEnglish), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Slope, Language Estimates') +
  theme_classic()

VSA_task_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_Taskspontaneousspeech), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(b_Environmentnaturalistic), fill="#A65628", color="#A65628",alpha=0.4) + 
  geom_density(aes(prior_b_Taskspontaneousspeech), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Slope, Task & Environment Estimates') +
  theme_classic()

VSA_age_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_Age_months), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(prior_b_Age_months), fill="steelblue", color="steelblue",alpha=0.7) +
  xlab('Slope, Age Estimate') +
  theme_classic()


VSA_pp_update <- plot_grid(VSA_intercept_pp_update, 
                                       VSA_language_pp_update, 
                                       VSA_task_pp_update, 
                                       VSA_age_pp_update, 
                                       VSA_sd_pp_update, 
                                       VSA_nu_pp_update,
                                       ncol = 1)
VSA_pp_update

#Articulation Rate:
#variables(AR_task_environment_language_age_m)
Posterior <- as_draws_df(AR_task_environment_language_age_m)


AR_intercept_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_Intercept), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(prior_Intercept), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Intercept') +
  ggtitle('Prior-Posterior Update Plots for Articulation Rate') +
  theme_classic() + theme(plot.title = element_text(hjust = 0.5, size=15))

AR_nu_pp_update <- ggplot(Posterior) +
  geom_density(aes(nu), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(prior_nu), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Nu') +
  theme_classic()

AR_sd_pp_update <- ggplot(Posterior) +
  geom_density(aes(sd_Language__Intercept), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(prior_sd_Language), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Standard Deviation of Studies') +
  theme_classic()

AR_language_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_LanguageBislama), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(b_LanguageBritishEnglish), fill="#E41A1C", color="#E41A1C",alpha=0.4) + 
  geom_density(aes(b_LanguageCanadianEnglish), fill="#984EA3", color="#984EA3",alpha=0.4) + 
  geom_density(aes(b_LanguageDanish), fill="#7570B3", color="#7570B3",alpha=0.4) + 
  geom_density(aes(b_LanguageJapanese), fill="#66A61E" , color="#66A61E" ,alpha=0.4) + 
  geom_density(aes(b_LanguageFrench), fill="#FFFF33", color="#FFFF33",alpha=0.4) + 
  geom_density(aes(b_LanguageCantoneseChinese), fill="#A65628", color="#A65628",alpha=0.4) + 
  geom_density(aes(`b_LanguageKenyan&Fijian`), fill="#F781BF", color="#F781BF",alpha=0.4) + 
  geom_density(aes(prior_b_LanguageUSEnglish), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Slope, Language Estimates') +
  theme_classic()

AR_task_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_Environmentnaturalistic), fill="#A65628", color="#A65628",alpha=0.4) + 
  geom_density(aes(prior_b_Environmentnaturalistic), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Slope, Task & Environment Estimates') +
  theme_classic()

AR_age_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_Age_months), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(prior_b_Age_months), fill="steelblue", color="steelblue",alpha=0.7) +
  xlab('Slope, Age Estimate') +
  theme_classic()


AR_pp_update <- plot_grid(AR_intercept_pp_update, 
                          AR_language_pp_update, 
                          AR_task_pp_update, 
                          AR_age_pp_update, 
                          AR_sd_pp_update, 
                          AR_nu_pp_update,
                          ncol = 1)

AR_pp_update

#Let's do the same for vowel duration:
#variables(VD_task_environment_language_age_m)
Posterior <- as_draws_df(VD_task_environment_language_age_m)

VD_intercept_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_Intercept), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(prior_Intercept), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Intercept') +
  ggtitle('Prior-Posterior Update Plots for Vowel Duration') +
  theme_classic() + theme(plot.title = element_text(hjust = 0.5, size=15))

VD_nu_pp_update <-ggplot(Posterior) +
  geom_density(aes(nu), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(prior_nu), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Nu') +
  theme_classic()

VD_sd_pp_update <- ggplot(Posterior) +
  geom_density(aes(sd_Language__Intercept), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(prior_sd_Language), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Standard Deviation of Studies') +
  theme_classic()

VD_language_pp_update <-ggplot(Posterior) +
  geom_density(aes(b_LanguageSwedish), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(b_LanguageBritishEnglish), fill="#E41A1C", color="#E41A1C",alpha=0.4) + 
  geom_density(aes(b_LanguageCanadianEnglish), fill="#984EA3", color="#984EA3",alpha=0.4) + 
  geom_density(aes(b_LanguageDanish), fill="#7570B3", color="#7570B3",alpha=0.4) + 
  geom_density(aes(b_LanguageJamaicanEnglish), fill="#666666", color="#666666",alpha=0.4) + 
  geom_density(aes(b_LanguageJapanese), fill="#66A61E" , color="#66A61E" ,alpha=0.4) + 
  geom_density(aes(b_LanguageNorwegian), fill="#FFFF33", color="#FFFF33",alpha=0.4) + 
  geom_density(aes(b_LanguageJapanese), fill="#A65628", color="#A65628",alpha=0.4) + 
  geom_density(aes(b_LanguageScottishEnglish), fill="#F781BF", color="#F781BF",alpha=0.4) + 
  geom_density(aes(prior_b_LanguageUSEnglish), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Slope, Language Estimates') +
  theme_classic()

VD_task_pp_update <-ggplot(Posterior) +
  geom_density(aes(b_Taskspontaneousspeech), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(b_Environmentnaturalistic), fill="#A65628", color="#A65628",alpha=0.4) + 
  geom_density(aes(prior_b_Taskspontaneousspeech), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Slope, Task & Environment Estimates') +
  theme_classic()

VD_age_pp_update <-ggplot(Posterior) +
  geom_density(aes(b_Age_months), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(prior_b_Age_months), fill="steelblue", color="steelblue",alpha=0.7) +
  xlab('Slope, Age Estimate') +
  theme_classic()


VD_pp_update <- plot_grid(VD_intercept_pp_update, 
                          VD_language_pp_update, 
                          VD_task_pp_update, 
                          VD_age_pp_update, 
                          VD_sd_pp_update, 
                          VD_nu_pp_update,
                          ncol = 1)
VD_pp_update

#And for F0 variability:
Posterior <- as_draws_df(F0V_task_environment_language_age_m)

F0V_intercept_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_Intercept), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(prior_Intercept), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Intercept') +
  ggtitle(expression(paste("Prior-Posterior Update Plots for ", italic(f)[o], " Variability"))) +
  theme_classic() + theme(plot.title = element_text(hjust = 0.5, size=15))

F0V_nu_pp_update <- ggplot(Posterior) +
  geom_density(aes(nu), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(prior_nu), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Nu') +
  theme_classic()

F0V_sd_pp_update <- ggplot(Posterior) +
  geom_density(aes(sd_Language__Intercept), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(prior_sd_Language), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Standard Deviation of Studies') +
  theme_classic()

F0V_language_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_LanguageSwedish), fill="#FC4E07", color="#FC4E07",alpha=0.4) + 
  geom_density(aes(b_LanguageBritishEnglish), fill="#E41A1C", color="#E41A1C",alpha=0.4) + 
  geom_density(aes(b_LanguageCanadianEnglish), fill="#984EA3", color="#984EA3",alpha=0.4) + 
  geom_density(aes(b_LanguageDanish), fill="#7570B3", color="#7570B3",alpha=0.4) + 
  geom_density(aes(b_LanguageBislama), fill="#666666", color="#666666",alpha=0.4) + 
  geom_density(aes(b_LanguageJapanese), fill="#66A61E" , color="#66A61E" ,alpha=0.4) + 
  geom_density(aes(b_LanguageNorwegian), fill="#FFFF33", color="#FFFF33",alpha=0.4) + 
  geom_density(aes(b_LanguageJapanese), fill="#A65628", color="#A65628",alpha=0.4) + 
  geom_density(aes(b_LanguageScottishEnglish), fill="#F781BF", color="#F781BF",alpha=0.4) + 
  geom_density(aes(prior_b_LanguageUSEnglish), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Slope, Language Estimates') +
  theme_classic()

F0V_task_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_Taskspontaneousspeech), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(b_Environmentnaturalistic), fill="#A65628", color="#A65628",alpha=0.4) + 
  geom_density(aes(prior_b_Taskspontaneousspeech), fill="steelblue", color="steelblue",alpha=0.6) +
  xlab('Slope, Task & Environment Estimates') +
  theme_classic()

F0V_age_pp_update <- ggplot(Posterior) +
  geom_density(aes(b_Age_months), fill="#FC4E07", color="#FC4E07",alpha=0.4) +
  geom_density(aes(prior_b_Age_months), fill="steelblue", color="steelblue",alpha=0.7) +
  xlab('Slope, Age Estimate') +
  theme_classic()


F0V_pp_update <- plot_grid(F0V_intercept_pp_update, 
                           F0V_language_pp_update, 
                           F0V_task_pp_update, 
                           F0V_age_pp_update, 
                           F0V_sd_pp_update, 
                           F0V_nu_pp_update,
                           ncol = 1)
F0V_pp_update
```


```{r, fig.width=12, fig.height=17}
#Collect in panel:
pp_update_plots <- plot_grid(F0_pp_update,
                             F0V_pp_update,
                             VSA_pp_update,
                             AR_pp_update,
                             VD_pp_update,
                             ncol = 2)
pp_update_plots
```

16: Heatmap overview of estimates
---------------

```{r}
#Make heatmap of meta-analytic estimates:
F0_age_language_model_data <- readRDS('models/F0_task_environment_language_age_report.rds')
c_eff <- conditional_effects(F0_age_language_model_data)
F0_age_language_model_data_heat <- c_eff$Language

F0_heatmap_data <- F0_age_language_model_data_heat %>%
  mutate(language = effect1__) %>%
  mutate(estimate = estimate__) %>%
  mutate(measure = "fo") %>%
  select(language, estimate, measure)

VSA_age_language_model_data <- readRDS('models/VSA_environment_report.rds')
c_eff <- conditional_effects(VSA_age_language_model_data)
VSA_age_language_model_data_heat <- c_eff$Language

VSA_heatmap_data <- VSA_age_language_model_data_heat %>%
  mutate(language = effect1__) %>%
  mutate(estimate = estimate__) %>%
  mutate(measure = "Vowel Space Area") %>%
  select(language, estimate, measure)

AR_age_language_model_data <- readRDS('models/AR_task_report.rds')
c_eff <- conditional_effects(AR_age_language_model_data)
AR_age_language_model_data_heat <- c_eff$Language

test <- tibble(language = AR_age_language_model_data_heat$Language, 
       estimate = paste(round(AR_age_language_model_data_heat$estimate__, 2), "[", round(AR_age_language_model_data_heat$lower__, 2), ";",  round(AR_age_language_model_data_heat$upper__, 2), "]"))

#note that we shift the articulation rate to display positive values:
AR_heatmap_data <- AR_age_language_model_data_heat %>%
  mutate(language = effect1__) %>%
  mutate(estimate = estimate__) %>%
  mutate(measure = "Articulation Rate") %>%
  select(language, estimate, measure) 

VD_age_language_model_data <- readRDS('models/VD_age_language_report.rds')
c_eff <- conditional_effects(VD_age_language_model_data)
VD_age_language_model_data_heat <- c_eff$Language

VD_heatmap_data <- VD_age_language_model_data_heat %>%
  mutate(language = effect1__) %>%
  mutate(estimate = estimate__) %>%
  mutate(measure = "Vowel Duration") %>%
  select(language, estimate, measure) 


F0V_age_language_model_data <- readRDS('models/F0V_task_report.rds')
c_eff <- conditional_effects(F0V_age_language_model_data)
F0V_age_language_model_data_heat <- c_eff$Language

F0V_heatmap_data <- F0V_age_language_model_data_heat %>%
  mutate(language = effect1__) %>%
  mutate(estimate = estimate__) %>%
  mutate(measure = "fo Variability") %>%
  select(language, estimate, measure)

heatmap_data <- rbind(F0_heatmap_data,
                      VSA_heatmap_data,
                      AR_heatmap_data,
                      VD_heatmap_data,
                      F0V_heatmap_data) 

heatmap_data <- heatmap_data %>%
  mutate(language = as.character(language)) %>%
  mutate(language = ifelse(language == "USEnglish", "US English", language)) %>%
  mutate(language = ifelse(language == "SriLankanTamil", "Sri Lankan Tamil", language)) %>%
  mutate(language = ifelse(language == "ScottishEnglish", "Scottish English", language)) %>%
  mutate(language = ifelse(language == "NewZealandEnglish", "New Zealand English", language)) %>%
  mutate(language = ifelse(language == "MandarinChinese", "Mandarin Chinese", language)) %>%
  mutate(language = ifelse(language == "KenyanFijian", "Kenyan/Fijian", language)) %>%
  mutate(language = ifelse(language == "FinnishSwedish", "Finnish/Swedish", language)) %>%
  mutate(language = ifelse(language == "CantoneseChinese", "Cantonese Chinese", language)) %>%
  mutate(language = ifelse(language == "CanadianEnglish", "Canadian English", language)) %>%
  mutate(language = ifelse(language == "BritishEnglish", "British English", language)) %>%
  mutate(language = ifelse(language == "JamaicanEnglish", "Jamaican English", language)) %>%
  mutate(language = ifelse(language == "QuechuaAchuar", "Quechua/Achuar", language)) %>%
  mutate(language = ifelse(language == "GuyaneseCreole", "Guyanese Creole", language)) %>%
  mutate(language = ifelse(language == "QuicheMayan", "Quiche Mayan", language)) %>%
  mutate(language = ifelse(language == "AustralianEnglish", "Australian English", language))
  

heatmap_data_family <- heatmap_data %>%
  mutate(measure = factor(measure, levels = c("fo", "fo Variability", "Vowel Space Area", "Articulation Rate", "Vowel Duration")))


heatmap_plot <- ggplot(data = heatmap_data_family, aes(y = reorder(language, desc(language)), 
                                                       x = measure, fill = estimate)) +
  geom_tile(col = "white",
            lwd = 1.5,
            linetype = 1) +
  scale_fill_gradient2(low = "steelblue", mid = "white", high = "#FC4E07", 
                       name = " Effect\n  Size\nEstimate") +
  geom_text(aes(label = round(estimate, 2)), color = "black", size = 4) +
  xlab('Acoustic Measure') +
  ylab('Language') +
  ggtitle('Heatmap of Acoustic Measures across Languages') +
  theme_bw()

heatmap_plot <- heatmap_plot + 
  theme(plot.title = element_text(hjust = 0.5, size = 17),
        legend.position="bottom",legend.direction="horizontal",
        axis.text.x = element_text(size = 15),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15)) +
  guides(fill = guide_colourbar(barwidth = 20,
                                barheight = 0.5,
                                label.hjust = 0.5,
                                ticks = FALSE,
                                label = T))
heatmap_plot
```

17: Prior Sensitivity Checks for Age Slopes
---------------

The following ten chunks are for the age slope of the models:

```{r, eval=FALSE}
#code to loop through sd of slope prior:
priSD <- seq(0.005, 0.2, length.out = 10)
priorsN <- priors1

#create empty sets to store output of the loop:
post_pred <- c()
post_pred_lci <- c()
post_pred_uci <- c()
evidence_ratio <- c()

for (i in 1:length(priSD)) {
  priorsN[4,] <- set_prior(paste0("normal(0, ", priSD[i],")"), class = "b", coef = "Age_months")
  model_for_loop <- brm(baseline_te,
                        data   = data_F0_final, 
                        family = student, 
                        prior  = priorsN, 
                        sample_prior = T,
                        warmup = 1000, 
                        iter   = 5000, 
                        cores  = 64,
                        chains = 2,
                        #backend = "cmdstanr",
                        #threads = threading(2),
                        save_pars = save_pars(all = TRUE),
                        control = list(adapt_delta   = 0.99, 
                                       max_treedepth = 15))
  
  post_preds <- spread_draws(model_for_loop, b_Age_months)
  post_pred[i] <- median(post_preds$b_Age_months)
  post_pred_lci[i] <- quantile(post_preds$b_Age_months, prob = 0.025)
  post_pred_uci[i] <- quantile(post_preds$b_Age_months, prob = 0.975)
  
  evidence_ratio[i] <- hypothesis(model_for_loop, "Age_months < 0")$hypothesis$Evid.Ratio
}

slope_prior_robustness_F0 <- data.frame(priSD, post_pred, post_pred_lci, post_pred_uci, evidence_ratio)
write.csv(slope_prior_robustness_F0, file = 'robustness_tests/slope_prior_robustness_F0.csv')
```

```{r}
slope_prior_robustness_F0 <- read.csv('robustness_tests/slope_prior_robustness_F0.csv')

slope_prior_robustness_F0_plot <- 
  ggplot() +
  geom_vline(xintercept = 0.05, alpha = 0.7, linetype = 2) +
  geom_point(data = slope_prior_robustness_F0, aes(x=priSD, y=post_pred), 
             size = 3, color = "black") +
  geom_point(data = slope_prior_robustness_F0, aes(x=priSD, y=post_pred), 
             size = 2, color = "#FC4E07") +
  geom_errorbar(data = slope_prior_robustness_F0, aes(x = priSD, ymin = post_pred_lci, 
                                                      ymax = post_pred_uci), color = "steelblue") +
  labs(x="Standard Deviation of Prior for Age", 
       y="Posterior Estimate for Age",
       title=expression(paste("Prior Sensitivity Analysis for Age Slope of ", italic(f)[o]))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
slope_prior_robustness_F0_plot


ER_slope_prior_robustness_F0_plot <- 
  ggplot() +
  geom_vline(xintercept = 0.05, alpha = 0.7, linetype = 2) +
  geom_point(data = slope_prior_robustness_F0, aes(x=priSD, y=evidence_ratio), 
             size = 3, color = "black") +
  geom_point(data = slope_prior_robustness_F0, aes(x=priSD, y=evidence_ratio), 
             size = 2, color = "#FC4E07") +
  labs(x="Standard Deviation of Prior for Age", 
       y="Age < 0",
       title=expression(paste("Prior Sensitivity Analysis - ER for Age Slope of ", italic(f)[o]))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
ER_slope_prior_robustness_F0_plot
```

```{r, eval=FALSE}
#code to loop through sd of slope prior:
priSD <- seq(0.005, 0.2, length.out = 10)
priorsN <- priors1

#create empty sets to store output of the loop:
post_pred <- c()
post_pred_lci <- c()
post_pred_uci <- c()
evidence_ratio <- c()

for (i in 1:length(priSD)) {
  priorsN[4,] <- set_prior(paste0("normal(0, ", priSD[i],")"), class = "b", coef = "Age_months")
  model_for_loop <- brm(baseline_te,
                        data   = data_VSA_final, 
                        family = student, 
                        prior  = priorsN, 
                        sample_prior = T,
                        warmup = 1000, 
                        iter   = 5000, 
                        cores  = 64,
                        chains = 2,
                        #backend = "cmdstanr",
                        #threads = threading(2),
                        save_pars = save_pars(all = TRUE),
                        control = list(adapt_delta   = 0.99, 
                                       max_treedepth = 15))
  
  post_preds <- spread_draws(model_for_loop, b_Age_months)
  post_pred[i] <- median(post_preds$b_Age_months)
  post_pred_lci[i] <- quantile(post_preds$b_Age_months, prob = 0.025)
  post_pred_uci[i] <- quantile(post_preds$b_Age_months, prob = 0.975)
  evidence_ratio[i] <- hypothesis(model_for_loop, "Age_months < 0")$hypothesis$Evid.Ratio
}

slope_prior_robustness_VSA <- data.frame(priSD, post_pred, post_pred_lci, post_pred_uci, evidence_ratio)
write.csv(slope_prior_robustness_VSA, file = 'robustness_tests/slope_prior_robustness_VSA.csv')
```

```{r}
slope_prior_robustness_VSA <- read.csv('robustness_tests/slope_prior_robustness_VSA.csv')

slope_prior_robustness_VSA_plot <- 
  ggplot() +
  geom_vline(xintercept = 0.05, alpha = 0.7, linetype = 2) +
  geom_point(data = slope_prior_robustness_VSA, aes(x=priSD, y=post_pred), 
             size = 3, color = "black") +
  geom_point(data = slope_prior_robustness_VSA, aes(x=priSD, y=post_pred), 
             size = 2, color = "#FC4E07") +
  geom_errorbar(data = slope_prior_robustness_VSA, aes(x = priSD, ymin = post_pred_lci, 
                                                       ymax = post_pred_uci), color = "steelblue") +
  labs(x="Standard Deviation of Prior for Age", 
       y="Posterior Estimate for Age",
       title="Prior Sensitivity Analysis for Age Slope of Vowel Space Area") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 14))
slope_prior_robustness_VSA_plot

ER_slope_prior_robustness_VSA_plot <- 
  ggplot() +
  geom_vline(xintercept = 0.05, alpha = 0.7, linetype = 2) +
  geom_point(data = slope_prior_robustness_VSA, aes(x=priSD, y=evidence_ratio), 
             size = 3, color = "black") +
  geom_point(data = slope_prior_robustness_VSA, aes(x=priSD, y=evidence_ratio), 
             size = 2, color = "#FC4E07") +
  labs(x="Standard Deviation of Prior for Age", 
       y="Age < 0",
       title=expression(paste("Prior Sensitivity Analysis - ER for Age Slope of Vowel Space"))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
ER_slope_prior_robustness_VSA_plot
```

```{r, eval=FALSE}
#code to loop through sd of slope prior:
priSD <- seq(0.005, 0.2, length.out = 10)
priorsN <- priors1

#create empty sets to store output of the loop:
post_pred <- c()
post_pred_lci <- c()
post_pred_uci <- c()
evidence_ratio <- c()

for (i in 1:length(priSD)) {
  priorsN[4,] <- set_prior(paste0("normal(0, ", priSD[i],")"), class = "b", coef = "Age_months")
  model_for_loop <- brm(baseline_e,
                        data   = data_AR_final, 
                        family = student, 
                        prior  = priorsN, 
                        sample_prior = T,
                        warmup = 1000, 
                        iter   = 5000, 
                        cores  = 64,
                        chains = 2,
                        #backend = "cmdstanr",
                        #threads = threading(2),
                        save_pars = save_pars(all = TRUE),
                        control = list(adapt_delta   = 0.99, 
                                       max_treedepth = 15))
  
  post_preds <- spread_draws(model_for_loop, b_Age_months)
  post_pred[i] <- median(post_preds$b_Age_months)
  post_pred_lci[i] <- quantile(post_preds$b_Age_months, prob = 0.025)
  post_pred_uci[i] <- quantile(post_preds$b_Age_months, prob = 0.975)
  evidence_ratio[i] <- hypothesis(model_for_loop, "Age_months > 0")$hypothesis$Evid.Ratio
}

slope_prior_robustness_AR <- data.frame(priSD, post_pred, post_pred_lci, post_pred_uci, evidence_ratio)
write.csv(slope_prior_robustness_AR, file = 'robustness_tests/slope_prior_robustness_AR.csv')
```

```{r}
slope_prior_robustness_AR <- read.csv('robustness_tests/slope_prior_robustness_AR.csv')

slope_prior_robustness_AR_plot <- 
  ggplot() +
  geom_vline(xintercept = 0.05, alpha = 0.7, linetype = 2) +
  geom_point(data = slope_prior_robustness_AR, aes(x=priSD, y=post_pred), 
             size = 3, color = "black") +
  geom_point(data = slope_prior_robustness_AR, aes(x=priSD, y=post_pred), 
             size = 2, color = "#FC4E07") +
  geom_errorbar(data = slope_prior_robustness_AR, aes(x = priSD, ymin = post_pred_lci, 
                                                      ymax = post_pred_uci), color = "steelblue") +
  labs(x="Standard Deviation of Prior for Age", 
       y="Posterior Estimate for Age",
       title="Prior Sensitivity Analysis for Age Slope of Articulation Rate") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
slope_prior_robustness_AR_plot

ER_slope_prior_robustness_AR_plot <- 
  ggplot() +
  geom_vline(xintercept = 0.05, alpha = 0.7, linetype = 2) +
  geom_point(data = slope_prior_robustness_AR, aes(x=priSD, y=evidence_ratio), 
             size = 3, color = "black") +
  geom_point(data = slope_prior_robustness_AR, aes(x=priSD, y=evidence_ratio), 
             size = 2, color = "#FC4E07") +
  labs(x="Standard Deviation of Prior for Age", 
       y="Age > 0",
       title=expression(paste("Prior Sensitivity Analysis - ER for Age Slope of Articulation Rate"))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
ER_slope_prior_robustness_AR_plot
```

```{r, eval=FALSE}
#code to loop through sd of slope prior:
priSD <- seq(0.005, 0.2, length.out = 10)
priorsN <- priors1

#create empty sets to store output of the loop:
post_pred <- c()
post_pred_lci <- c()
post_pred_uci <- c()
evidence_ratio <- c()

for (i in 1:length(priSD)) {
  priorsN[4,] <- set_prior(paste0("normal(0, ", priSD[i],")"), class = "b", coef = "Age_months")
  model_for_loop <- brm(baseline_te,
                        data   = data_VD_final, 
                        family = student, 
                        prior  = priorsN, 
                        sample_prior = T,
                        warmup = 1000, 
                        iter   = 5000, 
                        cores  = 2,
                        chains = 2,
                        #backend = "cmdstanr",
                        #threads = threading(2),
                        save_pars = save_pars(all = TRUE),
                        control = list(adapt_delta   = 0.99, 
                                       max_treedepth = 15))
  
  post_preds <- spread_draws(model_for_loop, b_Age_months)
  post_pred[i] <- median(post_preds$b_Age_months)
  post_pred_lci[i] <- quantile(post_preds$b_Age_months, prob = 0.025)
  post_pred_uci[i] <- quantile(post_preds$b_Age_months, prob = 0.975)
  evidence_ratio[i] <- hypothesis(model_for_loop, "Age_months < 0")$hypothesis$Evid.Ratio
}

slope_prior_robustness_VD <- data.frame(priSD, post_pred, post_pred_lci, post_pred_uci, evidence_ratio)
write.csv(slope_prior_robustness_VD, file = 'robustness_tests/slope_prior_robustness_VD.csv')
```

```{r}
slope_prior_robustness_VD <- read.csv('robustness_tests/slope_prior_robustness_VD.csv')

slope_prior_robustness_VD_plot <- 
  ggplot() +
  geom_vline(xintercept = 0.05, alpha = 0.7, linetype = 2) +
  geom_point(data = slope_prior_robustness_VD, aes(x=priSD, y=post_pred), 
             size = 3, color = "black") +
  geom_point(data = slope_prior_robustness_VD, aes(x=priSD, y=post_pred), 
             size = 2, color = "#FC4E07") +
  geom_errorbar(data = slope_prior_robustness_VD, aes(x = priSD, ymin = post_pred_lci, 
                                                      ymax = post_pred_uci), color = "steelblue") +
  labs(x="Standard Deviation of Prior for Age", 
       y="Posterior Estimate for Age",
       title="Prior Sensitivity Analysis for Age Slope of Vowel Duration") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
slope_prior_robustness_VD_plot

ER_slope_prior_robustness_VD_plot <- 
  ggplot() +
  geom_vline(xintercept = 0.05, alpha = 0.7, linetype = 2) +
  geom_point(data = slope_prior_robustness_VD, aes(x=priSD, y=evidence_ratio), 
             size = 3, color = "black") +
  geom_point(data = slope_prior_robustness_VD, aes(x=priSD, y=evidence_ratio), 
             size = 2, color = "#FC4E07") +
  labs(x="Standard Deviation of Prior for Age", 
       y="Age < 0",
       title=expression(paste("Prior Sensitivity Analysis - ER for Age Slope of Vowel Duration"))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
ER_slope_prior_robustness_VD_plot
```

```{r, eval=FALSE}
#code to loop through sd of slope prior:
priSD <- seq(0.005, 0.2, length.out = 10)
priorsN <- priors1

#create empty sets to store output of the loop:
post_pred <- c()
post_pred_lci <- c()
post_pred_uci <- c()
evidence_ratio <- c()

for (i in 1:length(priSD)) {
  priorsN[4,] <- set_prior(paste0("normal(0, ", priSD[i],")"), class = "b", coef = "Age_months")
  model_for_loop <- brm(baseline_te,
                        data   = data_F0V_final, 
                        family = student, 
                        prior  = priorsN, 
                        sample_prior = T,
                        warmup = 1000, 
                        iter   = 5000, 
                        cores  = 64,
                        chains = 2,
                        #backend = "cmdstanr",
                        #threads = threading(2),
                        save_pars = save_pars(all = TRUE),
                        control = list(adapt_delta   = 0.99, 
                                       max_treedepth = 15))
  
  post_preds <- spread_draws(model_for_loop, b_Age_months)
  post_pred[i] <- median(post_preds$b_Age_months)
  post_pred_lci[i] <- quantile(post_preds$b_Age_months, prob = 0.025)
  post_pred_uci[i] <- quantile(post_preds$b_Age_months, prob = 0.975)
  evidence_ratio[i] <- hypothesis(model_for_loop, "Age_months > 0")$hypothesis$Evid.Ratio
}

slope_prior_robustness_F0V <- data.frame(priSD, post_pred, post_pred_lci, post_pred_uci, evidence_ratio)
write.csv(slope_prior_robustness_F0V, file = 'robustness_tests/slope_prior_robustness_F0V.csv')
```

```{r}
slope_prior_robustness_F0V <- read.csv('robustness_tests/slope_prior_robustness_F0V.csv')

slope_prior_robustness_F0V_plot <- 
  ggplot() +
  geom_vline(xintercept = 0.05, alpha = 0.7, linetype = 2) +
  geom_point(data = slope_prior_robustness_F0V, aes(x=priSD, y=post_pred), 
             size = 3, color = "black") +
  geom_point(data = slope_prior_robustness_F0V, aes(x=priSD, y=post_pred), 
             size = 2, color = "#FC4E07") +
  geom_errorbar(data = slope_prior_robustness_F0V, aes(x = priSD, ymin = post_pred_lci, 
                                                       ymax = post_pred_uci), color = "steelblue") +
  labs(x="Standard Deviation of Prior for Age", 
       y="Posterior Estimate for Age",
       title=expression(paste("Prior Sensitivity Analysis for Age Slope of ", 
                              italic(f)[o], " Variability"))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
slope_prior_robustness_F0V_plot

ER_slope_prior_robustness_F0V_plot <- 
  ggplot() +
  geom_vline(xintercept = 0.05, alpha = 0.7, linetype = 2) +
  geom_point(data = slope_prior_robustness_F0V, aes(x=priSD, y=evidence_ratio), 
             size = 3, color = "black") +
  geom_point(data = slope_prior_robustness_F0V, aes(x=priSD, y=evidence_ratio), 
             size = 2, color = "#FC4E07") +
  labs(x="Standard Deviation of Prior for Age", 
       y="Age > 0",
       title=expression(paste("Prior Sensitivity Analysis - ER for Age Slope of ", 
                              italic(f)[o], " Variability"))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
ER_slope_prior_robustness_F0V_plot
```


18: Prior Robustness Checks for Intercepts
---------------
```{r, eval = FALSE}
priors1 <- c(prior(normal(0, 2.5), class = Intercept),
             prior(normal(1, 1), class = sd),
             prior(normal(0, 1), class = b),
             prior(normal(0, 0.05), class = b, coef = "Age_months"),
             prior(gamma(2, 0.1), class = nu))

#code to loop through sd of intercept prior:
priSD <- seq(0.1, 4, length.out = 10)
priorsN <- priors1

#create empty sets to store output of the loop:
post_pred <- c()
post_pred_lci <- c()
post_pred_uci <- c()
evidence_ratio <- c()

data_F0_final_report <- data_F0_final %>%
  select(Study, Language, Task, Environment, Age_months, Effect_Size, 
         Effect_Size_se, measurement_num, id_site) %>%
  drop_na() %>%
  mutate(Age_months = center_scale(Age_months)) %>%
  mutate(Language = str_replace_all(Language, "[^[:alnum:]]", ""))
  
for (i in 1:length(priSD)) {
  priorsN[1,] <- set_prior(paste0("normal(0, ", priSD[i],")"), class = "Intercept")
  model_for_loop <- brm(
    baseline_te,
    save_pars = save_pars(all = TRUE),
    data = data_F0_final_report, 
    family = student,
    prior = priorsN,
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))
  model_for_loop
  post_preds <- hypothesis(model_for_loop, "((Intercept*32 + LanguageBislama + LanguageBritishEnglish +
  LanguageCanadianEnglish + LanguageDanish + LanguageDutch + LanguageEnga + LanguageFinnishSwedish + LanguageFrench +
  LanguageGerman + LanguageHungarian + LanguageItalian + LanguageJamaicanEnglish + LanguageJapanese + LanguageKannada +
  LanguageKenyanFijian + LanguageKorean + LanguageMandarinChinese + LanguageMbendjele + LanguageMentawai + 
  LanguageNewZealandEnglish + LanguageNorwegian + LanguageNyangatom + LanguagePolish + LanguageQuechuaAchuar + 
  LanguageQuicheMayan + LanguageSpanish + LanguageSriLankanTamil + LanguageSwedish + LanguageTagalog + LanguageToposa + 
  LanguageTsimane + LanguageUSEnglish + Taskspontaneousspeech + Environmentnaturalistic)/32) > 0")
  
  post_pred[i] <- post_preds$hypothesis$Estimate
  post_pred_lci[i] <- post_preds$hypothesis$CI.Lower
  post_pred_uci[i] <- post_preds$hypothesis$CI.Upper
  evidence_ratio[i] <- post_preds$hypothesis$Evid.Ratio
}

intercept_prior_robustness_F0 <- data.frame(priSD, post_pred, post_pred_lci, post_pred_uci, evidence_ratio)
write.csv(intercept_prior_robustness_F0, file = 'robustness_tests/intercept_prior_robustness_F0.csv')
```

```{r}
intercept_prior_robustness_F0 <- read.csv('robustness_tests/intercept_prior_robustness_F0.csv')

intercept_prior_robustness_F0_plot <- 
  ggplot() +
  geom_vline(xintercept = 2.5, alpha = 0.7, linetype = 2) +
  geom_point(data = intercept_prior_robustness_F0, aes(x=priSD, y=post_pred), size = 3, color = "black") +
  geom_point(data = intercept_prior_robustness_F0, aes(x=priSD, y=post_pred), size = 2, color = "#FC4E07") +
  geom_errorbar(data = intercept_prior_robustness_F0, aes(x = priSD, ymin = post_pred_lci, ymax = post_pred_uci), color = "steelblue") +
  labs(x="Standard Deviation of Prior for Intercept", 
       y="Posterior Estimate for Intercept",
       title=expression(paste("Prior Sensitivity Analysis for Intercept of ", italic(f)[o]))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
intercept_prior_robustness_F0_plot

intercept_prior_robustness_F0 <- intercept_prior_robustness_F0 %>%
  mutate(evidence_ratio = as.factor(evidence_ratio))
  
ER_intercept_prior_robustness_F0_plot <- 
  ggplot() +
  geom_vline(xintercept = 2.5, alpha = 0.7, linetype = 2) +
  geom_point(data = intercept_prior_robustness_F0, aes(x=priSD, y=evidence_ratio), 
             size = 3, color = "black") +
  geom_point(data = intercept_prior_robustness_F0, aes(x=priSD, y=evidence_ratio), 
             size = 2, color = "#FC4E07") +
  labs(x="Standard Deviation of Prior for Intercept", 
       y="Intercept > 0",
       title=expression(paste("Prior Sensitivity Analysis - ER for Intercept of ", 
                              italic(f)[o]))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
ER_intercept_prior_robustness_F0_plot
```

```{r, eval = FALSE}
#code to loop through sd of intercept prior:
priSD <- seq(0.1, 4, length.out = 10)
priorsN <- priors1

#create empty sets to store output of the loop:
post_pred <- c()
post_pred_lci <- c()
post_pred_uci <- c()
evidence_ratio <- c()

data_VSA_final_report <- data_VSA_final %>%
  select(Study, Language, Environment, Task, Age_months, Effect_Size, Effect_Size_se, measurement_num, id_site) %>%
  drop_na() %>%
  mutate(Age_months = center_scale(Age_months)) %>%
  mutate(Language = str_replace_all(Language, "[^[:alnum:]]", ""))

for (i in 1:length(priSD)) {
  priorsN[1,] <- set_prior(paste0("normal(0, ", priSD[i],")"), class = "Intercept")
  model_for_loop <- brm(
    baseline_e,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_final_report, 
    family = student,
    prior = priorsN,
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))
  
  post_preds <- hypothesis(model_for_loop, "((Intercept*30 + LanguageBislama + 
                           LanguageBritishEnglish + LanguageCanadianEnglish + 
                           LanguageCantoneseChinese + LanguageDanish + LanguageDutch + 
                           LanguageEnga + LanguageFinnishSwedish + LanguageFrench + 
                           LanguageGerman + LanguageHungarian + LanguageJamaicanEnglish + 
                           LanguageJapanese + LanguageKannada + LanguageMandarinChinese + 
                           LanguageMbendjele + LanguageMentawai + LanguageNewZealandEnglish + 
                           LanguageNorwegian + LanguageNyangatom + LanguagePolish + 
                           LanguageQuechua + LanguageQuechuaAchuar + LanguageRussian + 
                           LanguageSpanish + LanguageSwedish + LanguageToposa + 
                           LanguageTsimane + LanguageUSEnglish + Environmentnaturalistic) / 30) > 0")
  post_pred[i] <- post_preds$hypothesis$Estimate
  post_pred_lci[i] <- post_preds$hypothesis$CI.Lower
  post_pred_uci[i] <- post_preds$hypothesis$CI.Upper
  evidence_ratio[i] <- post_preds$hypothesis$Evid.Ratio
}

intercept_prior_robustness_VSA <- data.frame(priSD, post_pred, post_pred_lci, post_pred_uci, evidence_ratio)
write.csv(intercept_prior_robustness_VSA, file = 'robustness_tests/intercept_prior_robustness_VSA.csv')
```

```{r}
intercept_prior_robustness_VSA <- read.csv('robustness_tests/intercept_prior_robustness_VSA.csv')

intercept_prior_robustness_VSA_plot <- 
  ggplot() +
  geom_vline(xintercept = 2.5, alpha = 0.7, linetype = 2) +
  geom_point(data = intercept_prior_robustness_VSA, aes(x=priSD, y=post_pred), size = 3, color = "black") +
  geom_point(data = intercept_prior_robustness_VSA, aes(x=priSD, y=post_pred), size = 2, color = "#FC4E07") +
  geom_errorbar(data = intercept_prior_robustness_VSA, aes(x = priSD, ymin = post_pred_lci, ymax = post_pred_uci), color = "steelblue") +
  labs(x="Standard Deviation of Prior for Intercept", 
       y="Posterior Estimate for Intercept",
       title="Prior Sensitivity Analysis for Intercept of Vowel Space Area") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
intercept_prior_robustness_VSA_plot

ER_intercept_prior_robustness_VSA_plot <- 
  ggplot() +
  geom_vline(xintercept = 2.5, alpha = 0.7, linetype = 2) +
  geom_point(data = intercept_prior_robustness_VSA, aes(x=priSD, y=evidence_ratio), size = 3, color = "black") +
  geom_point(data = intercept_prior_robustness_VSA, aes(x=priSD, y=evidence_ratio), size = 2, color = "#FC4E07") +
  labs(x="Standard Deviation of Prior for Intercept", 
       y="Intercept > 0",
       title=expression(paste("Prior Sensitivity Analysis - ER for Intercept of Vowel Space"))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
ER_intercept_prior_robustness_VSA_plot
```

```{r, eval = FALSE}
#code to loop through sd of intercept prior:
priSD <- seq(0.1, 4, length.out = 10)
priorsN <- priors1

#create empty sets to store output of the loop:
post_pred <- c()
post_pred_lci <- c()
post_pred_uci <- c()
evidence_ratio <- c()

data_AR_final_report <- data_AR_final %>%
  select(Study, Language, Task, Environment, Age_months, Effect_Size, Effect_Size_se, measurement_num, id_site) %>%
  drop_na() %>%
  mutate(Age_months = center_scale(Age_months)) %>%
  mutate(Language = str_replace_all(Language, "[^[:alnum:]]", ""))

for (i in 1:length(priSD)) {
  priorsN[1,] <- set_prior(paste0("normal(0, ", priSD[i],")"), class = "Intercept")
  model_for_loop <- brm(
    baseline_e,
    save_pars = save_pars(all = TRUE),
    data = data_AR_final_report, 
    family = student,
    prior = priorsN,
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))
  post_preds <- hypothesis(model_for_loop, "((Intercept*16 + LanguageBislama + LanguageBritishEnglish + LanguageCanadianEnglish + LanguageCantoneseChinese + LanguageDanish + LanguageDutch + LanguageFrench + LanguageGerman + LanguageItalian + LanguageJapanese + LanguageKenyanFijian + LanguageKorean + LanguageMandarinChinese + LanguageSriLankanTamil + LanguageTagalog + LanguageUSEnglish + Environmentnaturalistic) / 16) < 0")
  post_pred[i] <- post_preds$hypothesis$Estimate
  post_pred_lci[i] <- post_preds$hypothesis$CI.Lower
  post_pred_uci[i] <- post_preds$hypothesis$CI.Upper
  evidence_ratio[i] <- post_preds$hypothesis$Evid.Ratio
}

intercept_prior_robustness_AR <- data.frame(priSD, post_pred, post_pred_lci, post_pred_uci, evidence_ratio)
write.csv(intercept_prior_robustness_AR, file = 'robustness_tests/intercept_prior_robustness_AR.csv')
```

```{r}
intercept_prior_robustness_AR <- read.csv('robustness_tests/intercept_prior_robustness_AR.csv')

intercept_prior_robustness_AR_plot <- 
  ggplot() +
  geom_vline(xintercept = 2.5, alpha = 0.7, linetype = 2) +
  geom_point(data = intercept_prior_robustness_AR, aes(x=priSD, y=post_pred), size = 3, color = "black") +
  geom_point(data = intercept_prior_robustness_AR, aes(x=priSD, y=post_pred), size = 2, color = "#FC4E07") +
  geom_errorbar(data = intercept_prior_robustness_AR, aes(x = priSD, ymin = post_pred_lci, ymax = post_pred_uci), color = "steelblue") +
  labs(x="Standard Deviation of Prior for Intercept", 
       y="Posterior Estimate for Intercept",
       title="Prior Sensitivity Analysis for Intercept of Articulation Rate") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
intercept_prior_robustness_AR_plot

ER_intercept_prior_robustness_AR_plot <- 
  ggplot() +
  geom_vline(xintercept = 2.5, alpha = 0.7, linetype = 2) +
  geom_point(data = intercept_prior_robustness_AR, aes(x=priSD, y=evidence_ratio), size = 3, color = "black") +
  geom_point(data = intercept_prior_robustness_AR, aes(x=priSD, y=evidence_ratio), size = 2, color = "#FC4E07") +
  labs(x="Standard Deviation of Prior for Intercept", 
       y="Intercept < 0",
       title=expression(paste("Prior Sensitivity Analysis - ER for Intercept of Articulation Rate"))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
ER_intercept_prior_robustness_AR_plot
```

```{r, eval = FALSE}
#code to loop through sd of intercept prior:
priSD <- seq(0.1, 4, length.out = 10)
priorsN <- priors1

#create empty sets to store output of the loop:
post_pred <- c()
post_pred_lci <- c()
post_pred_uci <- c()
evidence_ratio <- c()

data_VD_final_report <- data_VD_final %>%
  select(Study, Language, Environment, Task, Age_months, Effect_Size, Effect_Size_se, measurement_num, id_site) %>%
  drop_na() %>%
  mutate(Age_months = center_scale(Age_months)) %>%
  mutate(Language = str_replace_all(Language, "[^[:alnum:]]", ""))

for (i in 1:length(priSD)) {
  priorsN[1,] <- set_prior(paste0("normal(0, ", priSD[i],")"), class = "Intercept")
  model_for_loop <- brm(
    baseline_f,
    save_pars = save_pars(all = TRUE),
    data = data_VD_final_report, 
    family = student,
    prior = priorsN,
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = 2,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))
  
  post_preds <- hypothesis(model_for_loop, "((Intercept*11 + LanguageBritishEnglish + LanguageCanadianEnglish + LanguageDanish + LanguageJamaicanEnglish + LanguageJapanese + LanguageMandarinChinese + LanguageNorwegian + LanguageScottishEnglish + LanguageSwedish + LanguageUSEnglish) / 11) > 0")
  post_pred[i] <- post_preds$hypothesis$Estimate
  post_pred_lci[i] <- post_preds$hypothesis$CI.Lower
  post_pred_uci[i] <- post_preds$hypothesis$CI.Upper
  evidence_ratio[i] <- post_preds$hypothesis$Evid.Ratio
}

intercept_prior_robustness_VD <- data.frame(priSD, post_pred, post_pred_lci, post_pred_uci, evidence_ratio)
write.csv(intercept_prior_robustness_VD, file = 'robustness_tests/intercept_prior_robustness_VD.csv')
```

```{r}
intercept_prior_robustness_VD <- read.csv('robustness_tests/intercept_prior_robustness_VD.csv')

intercept_prior_robustness_VD_plot <- 
  ggplot() +
  geom_vline(xintercept = 2.5, alpha = 0.7, linetype = 2) +
  geom_point(data = intercept_prior_robustness_VD, aes(x=priSD, y=post_pred), size = 3, color = "black") +
  geom_point(data = intercept_prior_robustness_VD, aes(x=priSD, y=post_pred), size = 2, color = "#FC4E07") +
  geom_errorbar(data = intercept_prior_robustness_VD, aes(x = priSD, ymin = post_pred_lci, ymax = post_pred_uci), color = "steelblue") +
  labs(x="Standard Deviation of Prior for Intercept", 
       y="Posterior Estimate for Intercept",
       title="Prior Sensitivity Analysis for Intercept of Vowel Duration") +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
intercept_prior_robustness_VD_plot

ER_intercept_prior_robustness_VD_plot <- 
  ggplot() +
  geom_vline(xintercept = 2.5, alpha = 0.7, linetype = 2) +
  geom_point(data = intercept_prior_robustness_VD, aes(x=priSD, y=evidence_ratio), size = 3, color = "black") +
  geom_point(data = intercept_prior_robustness_VD, aes(x=priSD, y=evidence_ratio), size = 2, color = "#FC4E07") +
  labs(x="Standard Deviation of Prior for Intercept", 
       y="Intercept > 0",
       title=expression(paste("Prior Sensitivity Analysis - ER for Intercept of Vowel Duration"))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
ER_intercept_prior_robustness_VD_plot
```

```{r, eval = FALSE}
#code to loop through sd of intercept prior:
priSD <- seq(0.1, 4, length.out = 10)
priorsN <- priors1

#create empty sets to store output of the loop:
post_pred <- c()
post_pred_lci <- c()
post_pred_uci <- c()
evidence_ratio <- c()

data_F0V_final_report <- data_F0V_final %>%
  select(Study, Language, Environment, Task, Age_months, Effect_Size, Effect_Size_se, measurement_num, id_site) %>%
  drop_na() %>%
  mutate(Age_months = center_scale(Age_months)) %>%
  mutate(Language = str_replace_all(Language, "[^[:alnum:]]", ""))

for (i in 1:length(priSD)) {
  priorsN[1,] <- set_prior(paste0("normal(0, ", priSD[i],")"), class = "Intercept")
  model_for_loop <- brm(
    baseline_t,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_final_report, 
    family = student,
    prior = priorsN,
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))
  
  post_preds <- hypothesis(model_for_loop, "((Intercept*33 + LanguageBislama + LanguageBritishEnglish + LanguageCanadianEnglish + LanguageCantoneseChinese + LanguageDanish + LanguageDutch + LanguageEnga + LanguageFinnishSwedish + LanguageFrench + LanguageGerman + LanguageHungarian + LanguageItalian + LanguageJapanese + LanguageKannada + LanguageKenyanFijian + LanguageKorean + LanguageMandarinChinese + LanguageMbendjele + LanguageMentawai + LanguageNewZealandEnglish + LanguageNorwegian + LanguageNyangatom + LanguagePolish + LanguageQuechua + LanguageQuechuaAchuar + LanguageScottishEnglish + LanguageSpanish + LanguageSriLankanTamil + LanguageSwedish + LanguageTagalog + LanguageToposa + LanguageTsimane + LanguageUSEnglish + Taskspontaneousspeech) / 33) > 0")
  post_pred[i] <- post_preds$hypothesis$Estimate
  post_pred_lci[i] <- post_preds$hypothesis$CI.Lower
  post_pred_uci[i] <- post_preds$hypothesis$CI.Upper
  evidence_ratio[i] <- post_preds$hypothesis$Evid.Ratio
}

intercept_prior_robustness_F0V <- data.frame(priSD, post_pred, post_pred_lci, post_pred_uci, evidence_ratio)
write.csv(intercept_prior_robustness_F0V, file = 'robustness_tests/intercept_prior_robustness_F0V.csv')
```

```{r}
intercept_prior_robustness_F0V <- read.csv('robustness_tests/intercept_prior_robustness_F0V.csv')

intercept_prior_robustness_F0V_plot <- 
  ggplot() +
  geom_vline(xintercept = 2.5, alpha = 0.7, linetype = 2) +
  geom_point(data = intercept_prior_robustness_F0V, aes(x=priSD, y=post_pred), size = 3, color = "black") +
  geom_point(data = intercept_prior_robustness_F0V, aes(x=priSD, y=post_pred), size = 2, color = "#FC4E07") +
  geom_errorbar(data = intercept_prior_robustness_F0V, aes(x = priSD, ymin = post_pred_lci, ymax = post_pred_uci), color = "steelblue") +
  labs(x="Standard Deviation of Prior for Intercept", 
       y="Posterior Estimate for Intercept",
       title=expression(paste("Prior Sensitivity Analysis for Intercept of ", italic(f)[o], " Variability"))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
intercept_prior_robustness_F0V_plot

ER_intercept_prior_robustness_F0V_plot <- 
  ggplot() +
  geom_vline(xintercept = 2.5, alpha = 0.7, linetype = 2) +
  geom_point(data = intercept_prior_robustness_F0V, aes(x=priSD, y=evidence_ratio), size = 3, color = "black") +
  geom_point(data = intercept_prior_robustness_F0V, aes(x=priSD, y=evidence_ratio), size = 2, color = "#FC4E07") +
  labs(x="Standard Deviation of Prior for Intercept", 
       y="Intercept > 0",
       title=expression(paste("Prior Sensitivity Analysis - ER for Intercept of ", italic(f)[o], " Variability"))) +
  theme_bw() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 15))
ER_intercept_prior_robustness_F0V_plot
```

19: Robustness Checks Plots
---------------

```{r}
#Create Panel with all of the prior sensitivity plots:
sensitivity_plot_age <- 
  plot_grid(slope_prior_robustness_F0_plot,
            slope_prior_robustness_F0V_plot,
            slope_prior_robustness_VSA_plot,
            slope_prior_robustness_AR_plot,
            slope_prior_robustness_VD_plot,
          ncol = 1)

sensitivity_plot_intercept <- 
  plot_grid(intercept_prior_robustness_F0_plot,
            intercept_prior_robustness_F0V_plot,
            intercept_prior_robustness_VSA_plot,
            intercept_prior_robustness_AR_plot,
            intercept_prior_robustness_VD_plot,
            ncol = 1)

ER_sensitivity_plot_age <- 
  plot_grid(ER_slope_prior_robustness_F0_plot,
            ER_slope_prior_robustness_F0V_plot,
            ER_slope_prior_robustness_VSA_plot,
            ER_slope_prior_robustness_AR_plot,
            ER_slope_prior_robustness_VD_plot,
          ncol = 1)

ER_sensitivity_plot_intercept <- 
  plot_grid(ER_intercept_prior_robustness_F0_plot,
            ER_intercept_prior_robustness_F0V_plot,
            ER_intercept_prior_robustness_VSA_plot,
            ER_intercept_prior_robustness_AR_plot,
            ER_intercept_prior_robustness_VD_plot,
            ncol = 1)

sensitivity_plot_all <- plot_grid(sensitivity_plot_intercept, 
                                  sensitivity_plot_age, 
                                  ncol = 2)

ER_sensitivity_plot_all <- plot_grid(ER_sensitivity_plot_intercept, 
                                     ER_sensitivity_plot_age,
                                     ncol = 2)
```

20: Models to report average effect size across languages & scaled age
---------------

We use this code to report a comparison to Table 1 in the original paper. First, reload data if necessary:

```{r}
data_F0_final <- readRDS(here("data/data_F0_final.RData"))
data_VSA_final <- readRDS(here("data/data_VSA_final.RData"))
data_AR_final <- readRDS(here("data/data_AR_final.RData"))
data_VD_final <- readRDS(here("data/data_VD_final.RData"))
data_F0V_final <- readRDS(here("data/data_F0V_final.RData"))

```


```{r}
center_scale <- function(x){
  scale(x, center = TRUE, scale = TRUE)}

data_F0_final_report <- data_F0_final %>%
  select(Study, Language, Task, Environment, Age_months, Effect_Size, Effect_Size_se, measurement_num, id_site) %>%
  drop_na() %>%
  mutate(Age_months = center_scale(Age_months)) %>%
  mutate(Language = str_replace_all(Language, "[^[:alnum:]]", ""))

F0_task_environment_language_age_report <- 
  brm(
    baseline_te,
    save_pars = save_pars(all = TRUE),
    data = data_F0_final_report, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "F0_task_environment_language_age_report_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

summary(F0_task_environment_language_age_report)

# sd of Study
sum_f0 <- summary(F0_task_environment_language_age_report)
sum_f0$random$`Language:id_site`

post_preds <- hypothesis(F0_task_environment_language_age_report, "((Intercept*32 + 
LanguageBislama + LanguageBritishEnglish + LanguageBritishEnglish + LanguageCanadianEnglish + 
LanguageDanish + LanguageDutch + LanguageEnga + LanguageFinnishSwedish + LanguageFrench +
LanguageGerman + LanguageHungarian + LanguageItalian + LanguageJamaicanEnglish + LanguageJapanese + LanguageKannada +
LanguageKenyanFijian + LanguageKorean + LanguageMandarinChinese + LanguageMbendjele + LanguageMentawai +
LanguageNewZealandEnglish + LanguageNorwegian + LanguageNyangatom + LanguagePolish + LanguageQuechuaAchuar +
LanguageQuicheMayan + LanguageSpanish + LanguageSriLankanTamil + LanguageSwedish + LanguageTagalog + LanguageToposa +
LanguageTsimane + LanguageUSEnglish + Taskspontaneousspeech + Environmentnaturalistic)/32) > 0")

post_preds

data_VSA_final_report <- data_VSA_final %>%
  select(Study, Language, Environment, Task, Age_months, Effect_Size, Effect_Size_se, measurement_num, id_site) %>%
  drop_na() %>%
  mutate(Age_months = center_scale(Age_months)) %>%
  mutate(Language = str_replace_all(Language, "[^[:alnum:]]", ""))

VSA_environment_report <- 
  brm(
    baseline_e,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_final_report, 
    family = student,
    prior = priors1,
    file = "models/replication/VSA_environment_report_rep",
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

summary(VSA_environment_report)

post_preds <- hypothesis(VSA_environment_report, "((Intercept*30 + LanguageBislama + 
                         LanguageBritishEnglish + LanguageCanadianEnglish + 
                         LanguageCantoneseChinese + LanguageDanish + LanguageDutch + 
                         LanguageEnga + LanguageFinnishSwedish + LanguageFrench + 
                         LanguageGerman + LanguageHungarian + LanguageJamaicanEnglish + 
                         LanguageJapanese + LanguageKannada + LanguageMandarinChinese + 
                         LanguageMbendjele + LanguageMentawai + LanguageNewZealandEnglish + 
                         LanguageNorwegian + LanguageNyangatom + LanguagePolish + 
                         LanguageQuechua + LanguageQuechuaAchuar + LanguageRussian + 
                         LanguageSpanish + LanguageSwedish + LanguageToposa + LanguageTsimane + 
                         LanguageUSEnglish + Environmentnaturalistic) / 30) > 0")

post_preds

# BS: Had to add id_site here to run the model
data_AR_final_report <- data_AR_final %>%
  select(Study, Language, Task, Environment, Age_months, Effect_Size, Effect_Size_se, measurement_num, id_site) %>%
  drop_na() %>%
  mutate(Age_months = center_scale(Age_months)) %>%
  mutate(Language = str_replace_all(Language, "[^[:alnum:]]", ""))

AR_task_report <- 
  brm(
    baseline_e,
    save_pars = save_pars(all = TRUE),
    data = data_AR_final_report, 
    family = student,
    prior = priors1,
    file = "models/replication/AR_task_report_rep",
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

summary(AR_task_report)
post_preds <- hypothesis(AR_task_report, "((Intercept*17 + LanguageBislama + LanguageBritishEnglish + LanguageCanadianEnglish + 
           LanguageCantoneseChinese + LanguageDanish + LanguageDutch + LanguageFrench + LanguageGerman + LanguageItalian + 
           LanguageJapanese + LanguageKenyanFijian + LanguageKorean + LanguageMandarinChinese + LanguageSriLankanTamil + 
           LanguageTagalog + LanguageUSEnglish) / 17) < 0")

post_preds

data_VD_final_report <- data_VD_final %>%
  select(Study, Language, Environment, Task, Age_months, Effect_Size, Effect_Size_se, measurement_num, id_site) %>%
  drop_na() %>%
  mutate(Age_months = center_scale(Age_months)) %>%
  mutate(Language = str_replace_all(Language, "[^[:alnum:]]", ""))

VD_age_language_report <- 
  brm(
    baseline_f,
    save_pars = save_pars(all = TRUE),
    data = data_VD_final_report, 
    family = student,
    prior = priors1,
    file = here("models/replication/VD_age_language_report_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

summary(VD_age_language_report)

post_preds <- hypothesis(VD_age_language_report, "((Intercept*11 + LanguageBritishEnglish + LanguageCanadianEnglish + LanguageDanish + LanguageJamaicanEnglish + 
           LanguageJapanese + LanguageMandarinChinese + LanguageNorwegian + LanguageScottishEnglish + LanguageSwedish + 
           LanguageUSEnglish) / 11) > 0")

post_preds

data_F0V_final_report <- data_F0V_final %>%
  select(Study, Language, Environment, Task, Age_months, Effect_Size, Effect_Size_se, measurement_num, id_site) %>%
  drop_na() %>%
  mutate(Age_months = center_scale(Age_months)) %>%
  mutate(Language = str_replace_all(Language, "[^[:alnum:]]", ""))

F0V_task_report <- 
  brm(
    baseline_t,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_final_report, 
    family = student,
    prior = priors1,
    file = "models/replication/F0V_task_report_rep",
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

summary(F0V_task_report)

post_preds <- hypothesis(F0V_task_report, "((Intercept*22 + LanguageBislama + LanguageBritishEnglish + LanguageCanadianEnglish + LanguageCantoneseChinese + LanguageDanish + LanguageDutch + LanguageFrench + LanguageGerman + LanguageHungarian + 
LanguageItalian + LanguageJapanese + LanguageKenyanFijian + LanguageKorean + LanguageMandarinChinese + 
LanguageNorwegian + LanguageScottishEnglish + LanguageSriLankanTamil + LanguageSwedish + LanguageTagalog + LanguageUSEnglish + Taskspontaneousspeech) / 22) > 0")

post_preds$hypothesis$Evid.Ratio
```


21: Model Comparison
---------------

```{r, eval = FALSE}
options(future.globals.maxSize= +Inf)

model_weights(F0_environment, F0_task, F0_task_environment_language_age, F0_age_language, F0_age, F0_language, F0_intercept, weights = "loo")
model_weights(VSA_environment, VSA_task, VSA_task_environment_language_age, VSA_age_language, VSA_age, VSA_language, VSA_intercept, weights = "loo")
model_weights(AR_environment, AR_task, AR_task_environment_language_age, AR_age_language, AR_age, AR_language, AR_intercept, weights = "loo")
model_weights(VD_environment, VD_task, VD_task_environment_language_age, VD_age_language, VD_age, VD_language, VD_intercept, weights = "loo")
model_weights(F0V_environment, F0V_task, F0V_task_environment_language_age, F0V_age_language, F0V_age, F0V_language, F0V_intercept, weights = "loo")
```



R1: Compare Estimates
---------------

We use a function to compare point estimates of the original models to the replicated models. 

```{r, eval = FALSE}
source(here("functions.R"))
diff_comp <- compare_point_ests("models", "models/replication", random_effects = TRUE)

# remove all NA
diff_comp_clean <- diff_comp[unlist(unname(lapply(diff_comp, function(x) !is.logical(x))))]

# df_diff_comp <- diff_comp_clean %>% 
#   bind_rows(., .id = "model")


# save resulting data frame
saveRDS(diff_comp_clean, here("output", "replication", "estimates_comparison.RDS"))
```

We reload the dataframe and show the results:
```{r, eval = TRUE}
diff_comp <- readRDS(here::here("output", "replication", "estimates_comparison.RDS"))
```

Present results for all fixed effects estimates:
```{r, eval = TRUE}
diff_point_estimates <- lapply(diff_comp, function(x) x$point_est)

df_diff_point <- diff_point_estimates |> 
  bind_rows(.id = "model") |> 
  mutate(model = gsub(".rds", "", model)) |> 
  mutate(model = gsub("_m", "", model))

df_diff_point |> 
  mutate(across(contains("Diff"),
                ~round(., 4))) |> 
  knitr::kable()
```


In addition, we can compare the random effects. Instead of looking at every individual random effect, we focus on the standard deviations of the random effects.
```{r, eval = TRUE}
df_diff_random <- lapply(diff_comp, function(x){
 x$random_effect |> 
    filter(grepl("sd_", Parameter))
}) |> 
  bind_rows(.id = "model") |> 
  mutate(model = gsub(".rds", "", model)) |> 
  mutate(model = gsub("_m", "", model))

df_diff_random |> 
  mutate(across(contains("Diff"),
                ~round(., 4))) |> 
  knitr::kable()

```


Also, compare evidence ratios by using each `hypothesis()` defined in section 21 of the original script:
```{r, eval = TRUE}
F0_hyp <- "((Intercept*32 + LanguageBislama + LanguageBritishEnglish + LanguageBritishEnglish + LanguageCanadianEnglish + LanguageDanish + LanguageDutch + LanguageEnga + LanguageFinnishSwedish + LanguageFrench + LanguageGerman + LanguageHungarian + LanguageItalian + LanguageJamaicanEnglish + LanguageJapanese + LanguageKannada + LanguageKenyanFijian + LanguageKorean + LanguageMandarinChinese + LanguageMbendjele + LanguageMentawai + LanguageNewZealandEnglish + LanguageNorwegian + LanguageNyangatom + LanguagePolish + LanguageQuechuaAchuar + LanguageQuicheMayan + LanguageSpanish + LanguageSriLankanTamil + LanguageSwedish + LanguageTagalog + LanguageToposa + LanguageTsimane + LanguageUSEnglish + Taskspontaneousspeech + Environmentnaturalistic)/32) > 0"

VSA_hyp <- "((Intercept*30 + LanguageBislama + LanguageBritishEnglish + LanguageCanadianEnglish + LanguageCantoneseChinese + LanguageDanish + LanguageDutch + LanguageEnga + LanguageFinnishSwedish + LanguageFrench +LanguageGerman + LanguageHungarian + LanguageJamaicanEnglish +               LanguageJapanese + LanguageKannada + LanguageMandarinChinese + LanguageMbendjele + LanguageMentawai + LanguageNewZealandEnglish + LanguageNorwegian + LanguageNyangatom + LanguagePolish +  LanguageQuechua + LanguageQuechuaAchuar + LanguageRussian + LanguageSpanish + LanguageSwedish + LanguageToposa + LanguageTsimane + LanguageUSEnglish + Environmentnaturalistic) / 30) > 0"

AR_hyp <- "((Intercept*17 + LanguageBislama + LanguageBritishEnglish + LanguageCanadianEnglish +  LanguageCantoneseChinese + LanguageDanish + LanguageDutch + LanguageFrench + LanguageGerman + LanguageItalian + LanguageJapanese + LanguageKenyanFijian + LanguageKorean + LanguageMandarinChinese + LanguageSriLankanTamil + LanguageTagalog + LanguageUSEnglish) / 17) < 0"

VD_hyp <- "((Intercept*11 + LanguageBritishEnglish + LanguageCanadianEnglish + LanguageDanish + LanguageJamaicanEnglish + LanguageJapanese + LanguageMandarinChinese + LanguageNorwegian + LanguageScottishEnglish + LanguageSwedish + LanguageUSEnglish) / 11) > 0"

F0V_hyp <- "((Intercept*22 + LanguageBislama + LanguageBritishEnglish + LanguageCanadianEnglish + LanguageCantoneseChinese + LanguageDanish + LanguageDutch + LanguageFrench + LanguageGerman + LanguageHungarian + LanguageItalian + LanguageJapanese + LanguageKenyanFijian + LanguageKorean + LanguageMandarinChinese + LanguageNorwegian + LanguageScottishEnglish + LanguageSriLankanTamil + LanguageSwedish + LanguageTagalog + LanguageUSEnglish + Taskspontaneousspeech) / 22) > 0"


# Combine into dataframe with the respective model name
df_evidence <- data.frame(
  best_model = c("F0_task_environment_language_age", 
                  "VSA_environment",
                  "AR_task",
                  "VD_age_language",
                  "F0V_task"),
  hypo = c(F0_hyp, VSA_hyp, AR_hyp, VD_hyp, F0V_hyp)
)

# Create columns for model names
# had to resort to absolute paths here due to a small bug on our server, 
# but these can be replaced by just deleting everything before /models/
df_evidence <- df_evidence |> 
  mutate(
    original_file = paste("~/ids-meta-replication/models/", best_model, "_report.rds", sep = ""),
    replication_file = paste("~/ids-meta-replication/models/replication/", best_model,   "_report_rep.rds", sep = "")
  )

# obtain evidence ratios
df_evidence <- df_evidence |> 
  mutate(
    original_evidence = map2_dbl(original_file, hypo, extract_evidence_ratio),
    replication_evidence = map2_dbl(replication_file, hypo, extract_evidence_ratio)
  )

# Display results
df_evidence |> 
  select(best_model, original_evidence, replication_evidence) |> 
  knitr::kable()

```


R2: Compare Best Models
---------------

Model fit assessment was originally conducted via "loo". In the file `robustness_replication.qmd`, we reproduced the model weight calculation and additionally calculated other model weights. 

First, we can check the model rank order in our replication of loo weights:
```{r, eval = TRUE}
# read in model weight results
weights_list <- readRDS(here("output", "replication", "weights_list.RDS")) 

# combine to df
df_weights <- lapply(weights_list, function(x){
  bind_rows(x, .id = "weights")
}) |> 
  bind_rows(.id = "model")
  

# only investigate loo weights here 
df_weights |> 
  filter(grepl("loo", weights)) |> 
  select(!weights) |> 
  pivot_longer(cols = !model, names_to = "predictors", values_to = "value") |> 
  group_by(model) |> 
  mutate(model_rank = rank(-value)) |> 
  mutate(value = round(value, 4)) |> 
  knitr::kable()

```






R3: Check "Robust Predictors"
---------------

In general, it was unclear to us what the terminology of "robust" predictors refers to. Here, we first check the single-predictor models for each predictor and feature to check if the 95\%-CrI of the predictor excludes zero.
```{r, eval=TRUE}
predictors <- c("age", "language", "environment", "task")
outcomes <- c("AR", "F0", "F0V", "VD", "VSA")

df_robust <- expand.grid(predictors, outcomes) |> 
  rename(
    predictors = Var1,
    outcomes = Var2
  )

# create file names
df_robust <- df_robust |> 
  mutate(filename = paste(here("models/replication/"), outcomes, "_", predictors, "_m_", "rep.rds", sep = ""))

# read in each data set, then check if the 95% CI excludes 0
check_ci <- function(filepath, ...){
  fit <- readRDS(filepath)
  sum_fit <- summary(fit)
  
  # check if CI of predictor excludes 0 
  # (which requires the product of the bounds to be positive)
  robust <- sum_fit$fixed$`l-95% CI`[[2]] * sum_fit$fixed$`u-95% CI`[[2]]
  robust > 0
}

# apply the function to the dataframe
df_robust_check <- df_robust |> 
  mutate(robust_pred = map(filename, check_ci))

# Prepare for plotting
df_robust_check |> 
  select(!filename) |> 
  mutate(robust_pred = unlist(robust_pred)) |> 
  pivot_wider(id_cols = outcomes, 
              names_from = predictors,
              values_from = robust_pred) |> 
  knitr::kable()

```

This does not reproduce the original results.

Alternatively, it might refer to the CrI of the predictor in the reported model, which we try now: 
```{r, eval = TRUE}
# F0: F0_task_environment_language_age_report
F0_rep <- readRDS(here("models", "replication", "F0_task_environment_language_age_report_rep.rds"))

summary_f0 <- summary(F0_rep)
summary_f0$fixed |> 
  knitr::kable()

# VSA: VSA_environment_report
VSA_rep <- readRDS(here("models", "replication", "VSA_environment_report_rep.rds"))

summary_VSA <- summary(VSA_rep)
summary_VSA$fixed |> 
  knitr::kable()
# AR: AR_task_report
# VD: VD_age_language_report
# F0V_task_report

```

This does not seem to be the case as well, so we stop after these two models. Alternatively, "robust" predictors might somehow be based on the evidence ratios, but this is also not clearly indicated in the manuscript.


# Session Info

```{r, eval = TRUE}
pander::pander(sessionInfo())
```






