---
title: "Robustness replication of *A Bayesian Meta-Analysis of the Acoustic Properties of Infant-Directed Speech*"
author: 
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Semih Can Aktepe
   orcid: 0000-0002-4776-9138
   affiliations: University of Marburg
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    fig-align: "center"
    embed-resoureces: true
execute:
  message: false
  warning: false
  eval: false
---

# 0. Preparation
Load the necessary packages and set the seed for reproducibility.
```{r setup}
library(brms)
library(tidyverse)
library(here)
# library(renv)
library(tidybayes)
library(RoBMA)
library(osfr)
library(bayesplot)
library(pander)
set.seed(35032)
``` 

# 1. Publication Bias 
Here, we will use Robust Bayesian Meta-Analyses to fit an ensemble of meta-analytic models, which will then be averaged with Bayesian Model Averaging. These models also estimate a publication bias adjustment.
https://fbartos.github.io/RoBMA/reference/RoBMA.reg.html
## F0
The authors selected the model with language, age, task & environment as predictors as the best model. 

TODO not sure how to deal with multiple imputation yet. Maybe average

TODO how to deal with hedges g
https://forum.cogsci.nl/discussion/7239/robma-random-effects-meta-analysis-with-meta-regression

### Intercept-Only
```{r f0-robma}
data_F0 <- readRDS(here("data/data_F0_multiple_final.RData"))

baseline_te <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + Age_months + 
                    Language + Environment + Task + (1 | Language/id_site/measurement_num))

# priors1 <- c(prior(normal(0, 2.5), class = Intercept),
#              prior(normal(1, 1), class = sd),
#              prior(normal(0, 1), class = b),
#              prior(normal(0, 0.05), class = b, coef = "Age_months"),
#              prior(gamma(2, 0.1), class = nu))

# TODO hedges g instead of d

F0_pub_bias <- RoBMA(
      y = data_F0[[1]]$Effect_Size, 
      se = data_F0[[1]]$Effect_Size_se, 
      study_ids = data_F0[[1]]$id_site,
      priors_bias = NULL,
      parallel = TRUE, 
      seed = 35037)

# Why is this a multivariate model?
saveRDS(F0_pub_bias, file = here("output/replication/F0_pub_bias.RDS"))
```
Regression



## VSA
The authors selected the model with age & language as predictors as the best model.

```{r vsa-robma}

```



## AR
The authors selected the model with task, age & language as predictors as the best model.

```{r ar-robma}

```

## VD
The authors selected the model with age & language as predictors as the best model.

```{r vd-robma}

```



## F0V
The authors selected the model with task, age & language as predictors as the best model.

```{r f0v-robma}

```



# 2. Compare Rank-Order of Model Weights


```{r}
# Load all relevant models into the environment
# TODO
# which ones are missing?
# 
file_names <- list.files(path = "models/replication/")
# F0:
# F0_environment, F0_task
# VSA: 
# VSA_environment, VSA_task
# AR: 
# AR_environment, AR_task
# VD:
# VD_environment, VD_task
# F0V:
# F0V_environment, F0V_task
```

First estimate the missing models, using the same prior specification as used in the models with language as predictor, but using the same random effects as in all priors. It is unclear to us why the random effects structure was changed for language. 
Environment as predictor: 
```{r}
baseline_envir <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + Environment + (1 | Language/id_site/measurement_num))
priors2 <- c(prior(normal(0, 2.5), class = Intercept),
             prior(normal(1, 1), class = sd),
             prior(normal(0, 1), class = b),
             prior(gamma(2, 0.1), class = nu))

F0_environment_m <- 
  brm_multiple(
    baseline_envir,
    save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "F0_environment_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

VSA_environment_m <- 
  brm_multiple(
    baseline_envir,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "VSA_environment_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

AR_environment_m <- 
  brm_multiple(
    baseline_envir,
    save_pars = save_pars(all = TRUE),
    data = data_AR_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "AR_environment_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

VD_environment_m <- 
  brm_multiple(
    baseline_envir,
    save_pars = save_pars(all = TRUE),
    data = data_VD_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "VD_environment_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(VD_environment_m, ndraws = 50)

F0V_environment_m <- 
  brm_multiple(
    baseline_envir,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "F0V_environment_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(F0V_language_m, ndraws = 50)
```


Task as predictor
```{r}
baseline_task <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + Task + (1 | Language/id_site/measurement_num))
priors2 <- c(prior(normal(0, 2.5), class = Intercept),
             prior(normal(1, 1), class = sd),
             prior(normal(0, 1), class = b),
             prior(gamma(2, 0.1), class = nu))

F0_task_m <- 
  brm_multiple(
    baseline_task,
    save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "F0_task_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

VSA_task_m <- 
  brm_multiple(
    baseline_task,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "VSA_task_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

AR_task_m <- 
  brm_multiple(
    baseline_task,
    save_pars = save_pars(all = TRUE),
    data = data_AR_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "AR_task_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

VD_task_m <- 
  brm_multiple(
    baseline_task,
    save_pars = save_pars(all = TRUE),
    data = data_VD_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "VD_task_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

pp_check(VD_task_m, ndraws = 50)

F0V_task_m <- 
  brm_multiple(
    baseline_task,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_multiple_final, 
    family = student,
    prior = priors2,
    file = here("models", "replication", "F0V_task_m_rep"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))
```


Now load in all relevant models to the environment:

TODO this is lacking "task_language_age" for every model, which was omitted from the original code. 
```{r, eval = FALSE}
options(future.globals.maxSize= +Inf)

file_names <- c("F0_environment_m_rep.rds", "F0_task_m_rep.rds", "F0_task_environment_language_age_m_rep.rds", 
                "F0_age_language_m_rep.rds", "F0_age_m_rep.rds", "F0_language_m_rep.rds", "F0_intercept_m_rep.rds")

final_names <- c("F0_environment", "F0_task", "F0_task_environment_language_age", 
                 "F0_age_language", "F0_age", "F0_language", "F0_intercept")

for (i in seq_along(file_names)) {
  model <- readRDS(paste0("models/replication/", file_names[i]))
  assign(final_names[i], model, envir = .GlobalEnv)
}
# weights_F0_loo <- model_weights(F0_environment, F0_task, F0_task_environment_language_age, F0_age_language, F0_age, F0_language, F0_intercept, weights = "loo")
# weights_F0_stack <- model_weights(F0_environment, F0_task, F0_task_environment_language_age, F0_age_language, F0_age, F0_language, F0_intercept, weights = "stacking")
# weights_F0_waic <- model_weights(F0_environment, F0_task, F0_task_environment_language_age, F0_age_language, F0_age, F0_language, F0_intercept, weights = "waic")
weights_F0_pmp <- post_prob(F0_environment, F0_task, F0_task_environment_language_age, F0_age_language, F0_age, F0_language, F0_intercept)

# VSA
file_names <- c("VSA_environment_m_rep.rds", "VSA_task_m_rep.rds", "VSA_task_environment_language_age_m_rep.rds", 
                "VSA_age_language_m_rep.rds", "VSA_age_m_rep.rds", "VSA_language_m_rep.rds", "VSA_intercept_m_rep.rds")

final_names <- c("VSA_environment", "VSA_task", "VSA_task_environment_language_age", 
                 "VSA_age_language", "VSA_age", "VSA_language", "VSA_intercept")

for (i in seq_along(file_names)) {
  model <- readRDS(paste0("models/replication/", file_names[i]))
  assign(final_names[i], model, envir = .GlobalEnv)
}
# weights_VSA_loo <- model_weights(VSA_environment, VSA_task, VSA_task_environment_language_age, VSA_age_language, VSA_age, VSA_language, VSA_intercept, weights = "loo")
# weights_VSA_stack <- model_weights(VSA_environment, VSA_task, VSA_task_environment_language_age, VSA_age_language, VSA_age, VSA_language, VSA_intercept, weights = "stacking")
# weights_VSA_waic <- model_weights(VSA_environment, VSA_task, VSA_task_environment_language_age, VSA_age_language, VSA_age, VSA_language, VSA_intercept, weights = "waic")
weights_VSA_pmp <- post_prob(VSA_environment, VSA_task, VSA_task_environment_language_age, VSA_age_language, VSA_age, VSA_language, VSA_intercept)

# AR
file_names <- c("AR_environment_m_rep.rds", "AR_task_m_rep.rds", "AR_task_environment_language_age_m_rep.rds", 
                "AR_age_language_m_rep.rds", "AR_age_m_rep.rds", "AR_language_m_rep.rds", "AR_intercept_m_rep.rds")

final_names <- c("AR_environment", "AR_task", "AR_task_environment_language_age", 
                 "AR_age_language", "AR_age", "AR_language", "AR_intercept")

for (i in seq_along(file_names)) {
  model <- readRDS(paste0("models/replication/", file_names[i]))
  assign(final_names[i], model, envir = .GlobalEnv)
}
# weights_AR_loo <- model_weights(AR_environment, AR_task, AR_task_environment_language_age, AR_age_language, AR_age, AR_language, AR_intercept, weights = "loo")
# weights_AR_stack <- model_weights(AR_environment, AR_task, AR_task_environment_language_age, AR_age_language, AR_age, AR_language, AR_intercept, weights = "stacking")
# # didn't work because of different dimensions of log lik matrix
# weights_AR_waic <- model_weights(AR_environment, AR_task, AR_task_environment_language_age, AR_age_language, AR_age, AR_language, AR_intercept, weights = "waic")
weights_AR_pmp <- post_prob(AR_environment, AR_task, AR_task_environment_language_age, AR_age_language, AR_age, AR_language, AR_intercept)

# VD
file_names <- c("VD_environment_m_rep.rds", "VD_task_m_rep.rds", "VD_task_environment_language_age_m_rep.rds", 
                "VD_age_language_m_rep.rds", "VD_age_m_rep.rds", "VD_language_m_rep.rds", "VD_intercept_m_rep.rds")

final_names <- c("VD_environment", "VD_task", "VD_task_environment_language_age", 
                 "VD_age_language", "VD_age", "VD_language", "VD_intercept")

for (i in seq_along(file_names)) {
  model <- readRDS(paste0("models/replication/", file_names[i]))
  assign(final_names[i], model, envir = .GlobalEnv)
}
# weights_VD_loo <- model_weights(VD_environment, VD_task, VD_task_environment_language_age, VD_age_language, VD_age, VD_language, VD_intercept, weights = "loo")
# stacking also did not work here
# weights_VD_stack <- model_weights(VD_environment, VD_task, VD_task_environment_language_age, VD_age_language, VD_age, VD_language, VD_intercept, weights = "stacking")
# weights_VD_waic <- model_weights(VD_environment, VD_task, VD_task_environment_language_age, VD_age_language, VD_age, VD_language, VD_intercept, weights = "waic")
# weights_VD_pmp <- post_prob(VD_environment, VD_task, VD_task_environment_language_age, VD_age_language, VD_age, VD_language, VD_intercept)

# F0V
file_names <- c("F0V_environment_m_rep.rds", "F0V_task_m_rep.rds", "F0V_task_environment_language_age_m_rep.rds", 
                "F0V_age_language_m_rep.rds", "F0V_age_m_rep.rds", "F0V_language_m_rep.rds", "F0V_intercept_m_rep.rds")

final_names <- c("F0V_environment", "F0V_task", "F0V_task_environment_language_age", 
                 "F0V_age_language", "F0V_age", "F0V_language", "F0V_intercept")

for (i in seq_along(file_names)) {
  model <- readRDS(paste0("models/replication/", file_names[i]))
  assign(final_names[i], model, envir = .GlobalEnv)
}
# weights_F0V_loo <- model_weights(F0V_environment, F0V_task, F0V_task_environment_language_age, F0V_age_language, F0V_age, F0V_language, F0V_intercept, weights = "loo")
weights_F0V_stack <- model_weights(F0V_environment, F0V_task, F0V_task_environment_language_age, F0V_age_language, F0V_age, F0V_language, F0V_intercept, weights = "stacking")
# weights_F0V_waic <- model_weights(F0V_environment, F0V_task, F0V_task_environment_language_age, F0V_age_language, F0V_age, F0V_language, F0V_intercept, weights = "waic")
# weights_F0V_pmp <- post_prob(F0V_environment, F0V_task, F0V_task_environment_language_age, F0V_age_language, F0V_age, F0V_language, F0V_intercept)

```

Cleaner code:

```{r}
options(future.globals.maxSize = +Inf)

load_models <- function(prefix) {
  file_names <- c("environment_m_rep.rds", "task_m_rep.rds", "task_environment_language_age_m_rep.rds", "task_language_age_m_rep.rds",
                  "age_language_m_rep.rds", "age_m_rep.rds", "language_m_rep.rds", "intercept_m_rep.rds")
  final_names <- c("environment", "task", "task_environment_language_age", "task_language_age", "age_language", "age", "language", "intercept")
  
  models <- list()
  for (i in seq_along(file_names)) {
    model <- readRDS(paste0("models/replication/", prefix, "_", file_names[i]))
    models[[final_names[i]]] <- model
  }
  return(models)
}

# safely compute weights
# TODO change to lapply probably
compute_weights_safe <- function(models, method) {
  tryCatch({
     do.call(model_weights, c(models, list(weights = method)))
  }, error = function(e) {
    message(paste("Error in model_weights with method", method, ": ", e$message))
    return(NULL)
  })
}

# compute all model weights for a given prefix
compute_model_weights <- function(prefix) {
  models <- load_models(prefix)
  
  weights <- list(
    loo = compute_weights_safe(models, "loo"),
    stacking = compute_weights_safe(models, "stacking"),
    waic = compute_weights_safe(models, "waic"),
    pmp = tryCatch({
      post_prob(models$environment, models$task, models$task_environment_language_age,
                models$task_language_age, models$age_language, models$age, models$language, models$intercept)
    }, error = function(e) {
      message(paste("Error in post_prob for prefix", prefix, ": ", e$message))
      return(NULL)
    })
  )
  
  rm(models) # Remove models from memory after calculation
  return(weights)
}

# iterate over each prefix
prefixes <- c("F0", "VSA", "AR", "F0V")
weights <- list()

for (prefix in prefixes) {
  message(paste("Computing weights for prefix:", prefix))
  weights[[prefix]] <- compute_model_weights(prefix)
}
```




Running this code for the first time results in an error for AR and VD: `Each log-likelihood matrix must have the same dimensions.` 
Upon inspection, we can find that some models have different dimensions, because `VD_intercept` and `AR_task_environment_language_age` were run with 10,000 instead of 5,000 iterations (without further explanation). We therefore re-ran these models with less iterations. 
```{r}
dim(log_lik(VD_age_language))
dim(log_lik(VD_intercept))  # has more dimensions

dim(log_lik(AR_age))
dim(log_lik(AR_task_environment_language_age)) # has more dimensions
```














Save all weights 
```{r}
weights_list <- list(
  weights_AR_waic = weights_AR_waic, 
  weights_AR_loo = weights_AR_loo,
  weights_F0_waic = weights_F0_waic,
  weights_F0_loo = weights_F0_loo,
  weights_F0V_waic = weights_F0V_waic,
  weights_F0V_loo = weights_F0V_loo,
  weights_VSA_waic = weights_VSA_waic,
  weights_VSA_loo = weights_VSA_loo,
  weights_VD_waic = weights_VD_waic,
  weights_VD_loo = weights_VD_loo
)

saveRDS(object = weights_list, 
        file = here("output/replication/weights_list.RDS"))

```

Reload all results
```{r}
weights_list <- readRDS(here("output/replication/weights_list.RDS"))
```


Then create a comparison table for model rank:
```{r}
rank(weights_list$weights_AR_waic)


```








# 3. Sampler Settings
The authors used relatively unorthodox sampler settings by choosing an `adapt_delta` of 0.99 and a `max_treedepth` of 20. We will compare fitting the models selected as best by the authors to the same models with more standard sampler settings.

## F0
The authors selected the model with language, age, task & environment as predictors as the best model. 

```{r f0-sampler}
data_F0_multiple_final <- readRDS(here("data/data_F0_multiple_final.RData"))

baseline_te <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + Age_months + 
                    Language + Environment + Task + (1 | Language/id_site/measurement_num))

priors1 <- c(prior(normal(0, 2.5), class = Intercept),
             prior(normal(1, 1), class = sd),
             prior(normal(0, 1), class = b),
             prior(normal(0, 0.05), class = b, coef = "Age_months"),
             prior(gamma(2, 0.1), class = nu))

F0_task_environment_language_age_m_sampler <- 
  brm_multiple(
    baseline_te,
    save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "replication", "sampler_check", "F0_task_environment_language_age_m_rep_sampler"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.8,
      max_treedepth = 10 ))

summary(F0_task_environment_language_age_m_sampler)
pp_check(F0_task_environment_language_age_m_sampler, ndraws = 100)

```

Now we check convergence: 
```{r}
lp_F0 <- bayesplot::log_posterior(F0_task_environment_language_age_m_sampler)
np_F0 <- bayesplot::nuts_params(F0_task_environment_language_age_m_sampler)
bayesplot::mcmc_nuts_divergence(np_F0, lp_F0)
```

```{r}
bayesplot::mcmc_pairs(F0_task_environment_language_age_m_sampler, np = np_F0, pars = c("Intercept","b_Age_months","b_LanguageBritishEnglish"),
           off_diag_args = list(size = 0.75))
```

```{r}
bayesplot::mcmc_parcoord(F0_task_environment_language_age_m_sampler, np = np_F0, pars = c("Intercept","b_Age_months","b_LanguageBritishEnglish"))
```



Compare results to the original model?

## VSA
The authors selected the model with age & language as predictors as the best model.

```{r vsa-sampler}
data_VSA_multiple_final <- readRDS(here("data/data_VSA_multiple_final.RData"))

baseline_f <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + 
                   Language + Age_months + (1 | Language/id_site/measurement_num))

VSA_age_language_m_sampler <- 
  brm_multiple(
    baseline_f,
    save_pars = save_pars(all = TRUE),
    data = data_VSA_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "sampler_check", "VSA_age_language_m_rep_sampler"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.80,
      max_treedepth = 10 ))
summary(VSA_age_language_m_sampler)
pp_check(VSA_age_language_m_sampler, ndraws = 100)
```

As there were no divergent transitions, we compare point estimates to the replicated model using the sampler settings as specified by the authors: 
```{r}
source("functions.R")
VSA_age_language_m <- readRDS(here("models/replication/VSA_age_language_m_rep.rds"))
diff_point_est(VSA_age_language_m_sampler, VSA_age_language_m)

```


## AR
The authors selected the model with task, age & language as predictors as the best model.

```{r ar-sampler}
data_AR_multiple_final <- readRDS(here("data/data_AR_multiple_final.RData"))
baseline_t <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + Age_months + 
                   Language + Task + (1 | Language/id_site/measurement_num))

AR_task_language_age_m_sampler <- 
  brm(
    baseline_t,
    save_pars = save_pars(all = TRUE),
    data = data_AR_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "sampler_check", "AR_task_language_age_m_rep_sampler"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.80,
      max_treedepth = 10 ))

summary(AR_task_language_age_m_sampler)
pp_check(AR_task_language_age_m_sampler, ndraws = 100)

```

## VD
The authors selected the model with age & language as predictors as the best model.

```{r vd-sampler}
data_VD_multiple_final <- readRDS(here("data/data_VD_multiple_final.RData"))
baseline_f <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + 
                   Language + Age_months + (1 | Language/id_site/measurement_num))

VD_age_language_m_sampler <- 
  brm_multiple(
    baseline_f,
    save_pars = save_pars(all = TRUE),
    data = data_VD_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "sampler_check", "VD_age_language_m_rep_sampler"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.80,
      max_treedepth = 10 ))

summary(VD_age_language_m_sampler)
pp_check(VD_age_language_m_sampler, ndraws = 100)

```



## F0V
The authors selected the model with task, age & language as predictors as the best model.

```{r f0v-sampler}
data_F0V_multiple_final <- readRDS(here("data/data_F0V_multiple_final.RData"))
F0V_task_language_age_m_sampler <- 
  brm_multiple(
    baseline_t,
    save_pars = save_pars(all = TRUE),
    data = data_F0V_multiple_final, 
    family = student,
    prior = priors1,
    file = here("models", "sampler_check", "F0V_task_language_age_m_rep_sampler"),
    sample_prior = T,
    iter = 5000, 
    warmup = 500,
    cores = cores,
    chains = 2,
    #backend = "cmdstanr",
    #threads = threading(2),
    control = list(
      adapt_delta = 0.99,
      max_treedepth = 20 ))

summary(F0V_task_language_age_m_sampler)
pp_check(F0V_task_language_age_m_sampler, ndraws = 100)

```

As there were no divergent transitions, we compare point estimates to the original model: 

```{r}

```


## Check the models with different sampler settings






# 4. Minor Things


# 5. Session Info

```{r}
pander::pander(sessionInfo())
```





