---
title: "Robustness replication of *A Bayesian Meta-Analysis of the Acoustic Properties of Infant-Directed Speech*"
author: 
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Semih Can Aktepe
   orcid: 0000-0002-4776-9138
   affiliations: University of Marburg
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    fig-align: "center"
    embed-resoureces: true
execute:
  message: false
  warning: false
  eval: true
---

# Preparation
Load the necessary packages and set the seed for reproducibility.
```{r setup}
library(brms)
library(tidyverse)
library(here)
# library(renv)
library(tidybayes)
#library(RoBMA)
library(osfr)
library(bayesplot)
library(pander)
library(knitr)
library(xtable)
set.seed(35032)
``` 


# Sampler Settings
The authors used relatively unorthodox sampler settings by choosing an `adapt_delta` of 0.99 and a `max_treedepth` of 20. We will compare fitting the models selected as best by the authors to the same models with more standard sampler settings, as this might give us an insight into potential issues with model complexity.

## F0
The authors selected the model with language, age, task & environment as predictors as the best model. 


We fit the model with typical settings on the first dataset to diagnose what is going wrong

```{r f0-sampler}
data_F0_multiple_final <- readRDS(here("data","data_F0_multiple_final.RData"))

baseline_te <- bf(Effect_Size | se(Effect_Size_se) ~ 1 + Age_months + 
                    Language + Environment + Task + (1 | Language/id_site/measurement_num))

priors1 <- c(brms::prior(normal(0, 2.5), class = Intercept),
             brms::prior(normal(1, 1), class = sd),
             brms::prior(normal(0, 1), class = b),
             brms::prior(normal(0, 0.05), class = b, coef = "Age_months"),
             brms::prior(gamma(2, 0.1), class = nu))

F0_task_environment_language_age_m_sampler <- 
  brm(
    baseline_te,
    save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final[[1]], 
    family = student,
    prior = priors1,
    sample_prior = T,
    iter = 1000, 
    warmup = 500,
    refresh = 1000,
    cores = 4,
    chains = 4
    )
```

```{r}
summary(F0_task_environment_language_age_m_sampler)
```

- Error variance is zero! We incorporate the residual in the model.

### Re-fit with random effects for measurement number dropped
```{r }
model_sigma_true <-  
  bf(Effect_Size | se(Effect_Size_se, sigma = TRUE) ~ 
       1 + Age_months + Language + Environment + Task + 
       (1 | Language/id_site/measurement_num))

priors1 <- c(brms::prior(normal(0, 2.5), class = Intercept),
             brms::prior(normal(1, 1), class = sd),
             brms::prior(normal(0, 1), class = b),
             brms::prior(normal(0, 0.05), class = b, coef = "Age_months"),
             brms::prior(gamma(2, 0.1), class = nu))

fit_sigma_true <- 
  brm(
    model_sigma_true,
    save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final[[1]], 
    family = student,
    prior = priors1,
    sample_prior = T,
    iter = 1000, 
    warmup = 500,
    refresh = 1000,
    cores = 4,
    chains = 4,
    backend = "cmdstanr"
    )
```

```{r}
summary(fit_sigma_true)
```

Let's make the priors a little less informative

```{r }
model_uninformative <-  
  bf(Effect_Size | se(Effect_Size_se, sigma = TRUE) ~ 
       1 + Age_months + Language + Environment + Task + 
       (1 | Language/id_site/measurement_num))

priors1 <- c(
  brms::prior(student_t(3, 0, 5), class = Intercept),
  brms::prior(student_t(3, 0, 2), class = sd),
  brms::prior(student_t(3, 0, 2), class = b),
  brms::prior(student_t(3, 0, .5), class = b, coef = "Age_months"),
  brms::prior(student_t(3, 1, 20), class = nu)
)

fit_uninformative <- 
  brm(
    model_uninformative,
    save_pars = save_pars(all = TRUE),
    data = data_F0_multiple_final[[1]], 
    family = student,
    prior = priors1,
    sample_prior = T,
    iter = 1000, 
    warmup = 500,
    refresh = 1000,
    cores = 4,
    chains = 4
    )
```

```{r}
summary(fit_uninformative)
```

```{r}
prior_summary(fit_uninformative)
```




















### Convergence Checks
Now we check convergence: 
```{r}
lp_F0 <- bayesplot::log_posterior(F0_task_environment_language_age_m_sampler)
np_F0 <- bayesplot::nuts_params(F0_task_environment_language_age_m_sampler)
bayesplot::mcmc_nuts_divergence(np_F0, lp_F0)
```

```{r}
bayesplot::mcmc_pairs(F0_task_environment_language_age_m_sampler, np = np_F0, pars = c("Intercept","b_Age_months","nu"),
           off_diag_args = list(size = 0.75))
```

```{r}
bayesplot::mcmc_parcoord(F0_task_environment_language_age_m_sampler, np = np_F0, pars = c("Intercept","b_Age_months","b_LanguageBritishEnglish"))
```

### Model Simplification






# Session Info

```{r}
pander::pander(sessionInfo())
```





